---
title: "Sardine MSE Result Notes"
author: "Robert Wildermuth"
date: "7/26/2021"
output: 
  pdf_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(r4ss)
library(ss3sim)
library(hablar) # just so I can convert a column data type
source("plot_comp_sampling.R")
source("plot_index_sampling.R")

source("age1plusDiagPlots.R")
source("FmsyDiagPlots.R")
source("recrDiagPlots.R")
source("catchDiagPlots.R")
source("compDiagPlots.R")
source("bDiagPlots.R")
```

# Evaluation of sardine cohort growth operating model

The following notes document the results of applying a 6 year projection to Peter Kuriyama's cohort growth Stock Synthesis model for Pacific sardine using {SSMSE}. The separate runs progress from a self test to applying additional sampling error in the SSMSE sampling module.

## Self test with only acoustic-trawl index specified

```{r OMselftest}
# read in SSMSE results summary
tsSumry <- read.csv("C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM/cohortGrowthselftest/results_ts_cohortGrowthselftest.csv")

# Get rid of duplicated SSB years
tsSumry <- na.omit(tsSumry)

# bring in simulated data for each iteration to plot with OM and EM vals
simDat <- data.frame()
for(i in c(2,4:9)){
  itDat <- SS_readdat(file = paste0("C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM/cohortGrowthselftest/",
                           i, "/cohortGrowthOMandEM_EM_2024/data.ss_new"),
                      version = "3.30")[["CPUE"]] %>%
            filter(index == 4) %>%
            mutate(iteration = i,
                   model_run = "cohortGrowthselftest_data")

  simDat <- rbind(simDat, itDat)
}
  
# simDat <- SS_readdat(file = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM/cohortGrowthselftest/2/cohortGrowthOMandEM_EM_2024/data.ss_new",
#                       version = "3.30")[["CPUE"]] %>%
#             filter(index == 4) %>%
#             mutate(#iteration = i,
#                    model_run = "cohortGrowthselftest_data")

# plots of simulated and estimated biomass trends per iteration
ggplot2::ggplot(data = subset(tsSumry, model_run %in% c("0_estimate_cohort_growh_OM",  
                                                      "cohortGrowthOMandEM_EM_2020",
                                                      "cohortGrowthOMandEM_EM_2021",
                                                      "cohortGrowthOMandEM_EM_2022",
                                                      "cohortGrowthOMandEM_EM_2023",
                                                      "cohortGrowthOMandEM_EM_2024")), 
                ggplot2::aes(x = year, y = SpawnBio)) +
  ggplot2::geom_vline(xintercept = 2019, color = "gray") +
  geom_point(data = simDat, mapping = aes(x = year, y = obs), shape = 4, color = "grey") +
  ggplot2::geom_line(ggplot2::aes(linetype = as.character(iteration), color = model_run))+
  ggplot2::scale_color_manual(values = c("#D65F00", rep("black", 4), "blue")) +
  ggplot2::scale_linetype_manual(values = rep("solid", 50)) +
  ggplot2::guides(linetype = FALSE) +
  ggplot2::facet_wrap(. ~ iteration) +
  ggplot2::theme_classic()

# plot of OM and EM and simulated data
indexPlot <- plot_index_sampling(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM/cohortGrowthselftest")
# !!RW: sampled_dataset are different among iterations

indexPlot # !RW: only getting last three iterations, but gets the point across 
```

### Summary plots of terminal year estimates
```{r}
termYr <- tsSumry %>% filter(model_run %in% c("0_estimate_cohort_growh_OM", 
                                              "cohortGrowthOMandEM_EM_init") | # or keep end years
                             year == as.numeric(regmatches(model_run, 
                                                           gregexpr("[[:digit:]]+", model_run))))

termYr <- termYr %>% mutate(model_run = as.character(model_run),
                            model_run = case_when(!model_run %in% c("0_estimate_cohort_growh_OM", 
                                                                    "cohortGrowthOMandEM_EM_init") ~"cohortGrowthOMandEM_EM_term",
                                                  TRUE ~ model_run))

ggplot2::ggplot(data = termYr, 
                ggplot2::aes(x = year, y = SpawnBio)) +
  ggplot2::geom_vline(xintercept = 2019, color = "gray") +
  geom_point(data = simDat, mapping = aes(x = year, y = obs), shape = 4, color = "grey") +
  ggplot2::geom_line(ggplot2::aes(linetype = as.character(iteration), color = model_run))+
  ggplot2::scale_color_manual(values = c("#D65F00", "black", rep("blue", 5))) +
  ggplot2::scale_linetype_manual(values = rep("solid", 50)) +
  ggplot2::guides(linetype = FALSE) +
  ggplot2::facet_wrap(. ~ iteration) +
  ggplot2::theme_classic()

relSSB_EMtoOM <- termYr %>% select(model_run, year, iteration, SpawnBio) %>%
                    pivot_wider(id_cols = c(year, iteration),
                                names_from = model_run, values_from = SpawnBio) %>%
                    rename(cohort_growth_OM = "0_estimate_cohort_growh_OM") %>%
                    mutate(diffSSB = case_when(is.na(cohortGrowthOMandEM_EM_term) ~ cohortGrowthOMandEM_EM_init - cohort_growth_OM,
                                               !is.na(cohortGrowthOMandEM_EM_term) ~ cohortGrowthOMandEM_EM_term - cohort_growth_OM))

relSSB_EMtoOM <- relSSB_EMtoOM %>% full_join(y = simDat, by = c("year", "iteration")) %>%
                    mutate(diffDat = obs - cohort_growth_OM)

ggplot(data = relSSB_EMtoOM, aes(x = year, y = diffSSB)) +
  ggplot2::geom_vline(xintercept = 2019, color = "gray") +
  geom_hline(yintercept = 0, color = "black") +
  geom_point(mapping = aes(x = year, y = diffDat), shape = 4, color = "grey") +
  ggplot2::geom_line(ggplot2::aes(linetype = as.character(iteration), color = 2))+
  #ggplot2::scale_color_manual(values = c("#D65F00", "black", rep("blue", 5))) +
  ggplot2::scale_linetype_manual(values = rep("solid", 50)) +
  ggplot2::guides(linetype = FALSE) +
  ggplot2::facet_wrap(. ~ iteration) +
  ggplot2::theme_classic()
```

### Plots of length and age composition
```{r}
# plot_comp_sampling(dir = "C:/Users/rwildermuth/Documents/FutureSeas/SardineMSE/cohortGrowthOMandEM/cohortGrowthselftest", comp_type = "agecomp")
# !!!Error: The comp database from the operating model has no rows, so must not have been any historical data in the OM.

outputSS <- SS_output(
  dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM/cohortGrowthselftest/2/cohortGrowthOMandEM_EM_2024",
  dir.mcmc = NULL,
  repfile = "Report.sso",
  compfile = "CompReport.sso")

SSplotComps(replist = outputSS, kind = "LEN")

SSplotComps(replist = outputSS, kind = "AGE") # nothing happens

# Try using r4ss supporting function
tmp <- SSMethod.TA1.8(fit = outputSS, type = "len", 
                      fleet = 4, fleetnames = outputSS[["FleetNames"]], datonly = FALSE, 
                                  printit = FALSE)
# doesn't show compositions by length

unique(outputSS[["lendbase"]]$Yr) # doesn't have data from projection years (2020-2024)
FleetNames <- outputSS[["FleetNames"]]

# try using ss3sim::get_compfit
# RW: function doesn't exist in the package? but it's in the index...
# get_compfit(report.file = outputSS, name = "len_comp_fit_table")

# run_SSMSE uses expected values for OM catch, so use these in figs
# RW: 'lendbase' only has observed years from historical time series
# termLenComps <- outputSS[["lendbase"]] %>% filter(Fleet == which(FleetNames == "AT_Survey")) %>%
#                   select(Yr, Seas, Fleet, Bin, Exp)

# Plot terminal age and length comps for OM and EM by iteration
termLenComps <- data.frame()
termAgeComps <- data.frame()

for(i in c(2,4:9)){
  outputSS <- SS_output(dir = paste0( "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM/cohortGrowthselftest/", 
                                     i, "/cohortGrowthOMandEM_EM_2024"),
                        dir.mcmc = NULL,
                        repfile = "Report.sso",
                        compfile = "CompReport.sso", verbose = FALSE, printstats = FALSE)
  
  EMLenComps <- outputSS[["batlen"]] %>% filter(Yr == 2024, Seas == 2, `Beg/Mid` == "B") %>%
                  pivot_longer(cols = c("6", "6.5", "7", "7.5", "8", "8.5", "9", "9.5", "10", "10.5", 
                                        "11", "11.5", "12", "12.5", "13", "13.5", "14", "14.5", "15", "15.5",
                                        "16", "16.5", "17", "17.5", "18", "18.5", "19", "19.5", "20", "20.5",
                                        "21", "21.5", "22", "22.5", "23", "23.5", "24", "24.5", "25", "25.5", 
                                        "26", "26.5", "27", "27.5", "28", "28.5", "29", "29.5", "30"),
                               names_to = "Bin", values_to = "Biomass") %>%
                  mutate(Bin = as.numeric(Bin),
                         model_run = "cohortGrowthOMandEM_EM_2024",
                         iteration = i)

  EMAgeComps <- outputSS[["batage"]] %>% filter(Yr == 2024, Seas == 2, `Beg/Mid` == "B") %>%
                  pivot_longer(cols = c("0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
                               names_to = "Age", values_to = "Biomass") %>%
                  mutate(Age = as.numeric(Age),
                         model_run = "cohortGrowthOMandEM_EM_2024",
                         iteration = i)
  
  OMoutputSS <- SS_output(dir = paste0( "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM/cohortGrowthselftest/", 
                                       i, "/0_estimate_cohort_growh_OM"),
                          dir.mcmc = NULL,
                          repfile = "Report.sso",
                          compfile = "CompReport.sso", verbose = FALSE, printstats = FALSE)

  OMLenComps <- OMoutputSS[["batlen"]] %>% filter(Yr == 2024, Seas == 2, `Beg/Mid` == "B") %>%
                  pivot_longer(cols = c("6", "6.5", "7", "7.5", "8", "8.5", "9", "9.5", "10", "10.5", 
                                        "11", "11.5", "12", "12.5", "13", "13.5", "14", "14.5", "15", "15.5",
                                        "16", "16.5", "17", "17.5", "18", "18.5", "19", "19.5", "20", "20.5",
                                        "21", "21.5", "22", "22.5", "23", "23.5", "24", "24.5", "25", "25.5", 
                                        "26", "26.5", "27", "27.5", "28", "28.5", "29", "29.5", "30"),
                               names_to = "Bin", values_to = "Biomass") %>%
                  mutate(Bin = as.numeric(Bin),
                         model_run = "0_estimate_cohort_growh_OM",
                         iteration = i)
  OMAgeComps <- OMoutputSS[["batage"]] %>% filter(Yr == 2024, Seas == 2, `Beg/Mid` == "B") %>%
                  pivot_longer(cols = c("0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
                               names_to = "Age", values_to = "Biomass") %>%
                  mutate(Age = as.numeric(Age),
                         model_run = "0_estimate_cohort_growh_OM",
                         iteration = i)
  termAgeComps <- rbind(termAgeComps, EMAgeComps, OMAgeComps)
  termLenComps <- rbind(termLenComps, EMLenComps, OMLenComps)
}

# RW: no composition data for last year because none provided in 'sample_struct_list' for run_SSMSE()
ggplot(termLenComps, mapping = aes(x = Bin, y = Biomass)) +
  geom_col() +
  facet_grid(cols = vars(model_run), rows = vars(iteration))


ggplot(termAgeComps, mapping = aes(x = Age, y = Biomass)) +
  geom_col() +
  facet_grid(cols = vars(model_run), rows = vars(iteration))
```

## Generalized functions applied to Self Test with AT only

Make some generalized functions to apply to different scenarios
```{r cohortSelfTest}
 
bDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM",
          scenario = "cohortGrowthselftest",
          termYr = 2024, surveyInx = 4)

compDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM",
              scenario = "cohortGrowthselftest",
              termYr = 2024)

# pull recruitment from summary dq
recrDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM",
              scenario = "cohortGrowthselftest", termYr = 2024)

#TotCatch_ in ss_summary.sso? or outputSS[["catch"]]
# outputSS <- SS_output(
#   dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM/cohortGrowthselftest/2/cohortGrowthOMandEM_EM_2024",
#   dir.mcmc = NULL,
#   repfile = "Report.sso",
#   compfile = "CompReport.sso", verbose = FALSE, printstats = FALSE)
# 
# catSmry <- outputSS[["catch"]] %>% group_by(Yr) %>%
#               # summarize totoal catch within year
#               dplyr::summarize(obsCat = sum(Obs),
#                                expCat = sum(Exp))

catchDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM",
              scenario = "cohortGrowthselftest", termYr = 2024)

FmsyDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM",
              scenario = "cohortGrowthselftest", termYr = 2024)

#SmryBio_ in ss_summary.sso? or outputSS[["timeseries"]]
# these aren't equal. SpawnBio matches between these files, but not outputSS[["timeseries"]]$Bio_smry

# outputSS[["timeseries"]] %>% select(Yr, Era, Seas, Bio_smry, `SmryBio_SX:1_GP:1`, SpawnBio)

age1plusDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM",
                  scenario = "cohortGrowthselftest", termYr = 2024)

```

## Self-test with acoustic-trawl and age and length comps specified in projection period

```{r OMself_wComps}
bDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM",
          scenario = "cohortGrowthself_compNsamp",
          termYr = 2024, surveyInx = 4)

compDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM",
              scenario = "cohortGrowthself_compNsamp",
              termYr = 2024, surveyInx = 4)

recrDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM",
              scenario = "cohortGrowthself_compNsamp", termYr = 2024)

catchDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM",
              scenario = "cohortGrowthself_compNsamp", termYr = 2024)

FmsyDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM",
              scenario = "cohortGrowthself_compNsamp", termYr = 2024)

age1plusDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMandEM",
              scenario = "cohortGrowthself_compNsamp", termYr = 2024)

```

## Test with AT and comp data and fixed parameter EM

```{r fixedEM_wComps}
bDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMfixedParamsEM",
          scenario = "cohortGrowth_compNsamp",
          termYr = 2024, surveyInx = 4)

compDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMfixedParamsEM",
              scenario = "cohortGrowth_compNsamp",
              termYr = 2024, surveyInx = 4)

recrDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMfixedParamsEM",
              scenario = "cohortGrowth_compNsamp", termYr = 2024)

catchDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMfixedParamsEM",
              scenario = "cohortGrowth_compNsamp", termYr = 2024)

FmsyDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMfixedParamsEM",
              scenario = "cohortGrowth_compNsamp", termYr = 2024)

age1plusDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMfixedParamsEM",
              scenario = "cohortGrowth_compNsamp", termYr = 2024)

# Look at growth and selectivity parameters
# outputSS <- SS_output(dir = file.path("C:/Users/rwildermuth/Documents/FutureSeas/SardineMSE/cohortGrowthOMfixedParamsEM",
#                                       "cohortGrowth_compNsamp", 1, "0_estimate_cohort_growh_OM"),
#                       dir.mcmc = NULL,
#                       repfile = "Report.sso",
#                       compfile = "CompReport.sso", verbose = FALSE, printstats = FALSE)
# SS_plots(outputSS, plot = c(1, 2, 16, 17, 20, 25, 26))
# 
# outputEM <- SS_output(dir = file.path("C:/Users/rwildermuth/Documents/FutureSeas/SardineMSE/cohortGrowthOMfixedParamsEM",
#                                       "cohortGrowth_compNsamp", 1, "cohortGrowthOMfixedParamsEM_EM_2024"),
#                       dir.mcmc = NULL,
#                       repfile = "Report.sso",
#                       compfile = "CompReport.sso", verbose = FALSE, printstats = FALSE)
# SS_plots(outputEM, plot = c(1, 2, 16, 17, 20, 25, 26))
```

## Constant growth OM with AT and comp data and fixed parameter EM

```{r constOMandEM_wComps}
bDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/constGrowthOMfixedParamsEM",
          scenario = "constGrowth_compNsamp",
          termYr = 2024, surveyInx = 4)

compDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/constGrowthOMfixedParamsEM",
              scenario = "constGrowth_compNsamp",
              termYr = 2024, surveyInx = 4)

recrDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/constGrowthOMfixedParamsEM",
              scenario = "constGrowth_compNsamp", termYr = 2024)

catchDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/constGrowthOMfixedParamsEM",
              scenario = "constGrowth_compNsamp", termYr = 2024)

FmsyDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/constGrowthOMfixedParamsEM",
              scenario = "constGrowth_compNsamp", termYr = 2024)

age1plusDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/constGrowthOMfixedParamsEM",
              scenario = "constGrowth_compNsamp", termYr = 2024)

```

## Sample size test with cohort growth OM model

```{r sampleSizeTest}
age1plusDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMfixedParamsEM",
                  scenario = "5pctAnnChangeNsamp10Model", termYr = 2028)

age1plusDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMfixedParamsEM",
                  scenario = "5pctAnnChangeNsamp20Model", termYr = 2028)

age1plusDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMfixedParamsEM",
                  scenario = "5pctAnnChangeNsamp40Model", termYr = 2028)

age1plusDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/cohortGrowthOMfixedParamsEM",
                  scenario = "5pctAnnChangeNsamp100Model", termYr = 2028)
```

## Marginal compositions OM and fixed selectivity EM with high data quality
```{r margComps_highDatQual}
bDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/margCompsOMfixedSelexEM",
          scenario = "margComps_highDatQual",
          termYr = 2028, surveyInx = 4)

compDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/margCompsOMfixedSelexEM",
              scenario = "margComps_highDatQual",
              termYr = 2028, surveyInx = 4)

recrDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/margCompsOMfixedSelexEM",
              scenario = "margComps_highDatQual", termYr = 2028)

catchDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/margCompsOMfixedSelexEM",
              scenario = "margComps_highDatQual", termYr = 2028)

FmsyDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/margCompsOMfixedSelexEM",
              scenario = "margComps_highDatQual", termYr = 2028)

age1plusDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/scenarioRuns/margCompsOMfixedSelexEM",
              scenario = "margComps_highDatQual", termYr = 2028)
```

## Self test of constant growth and selectivity as OM and EM with moderate data quality starting 2001 applying HCR1
```{r constGrowth2001OMandEM_RandRecHCR1}
bDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
          scenario = "constGrowth2001OMandEM_RandRecHCR1",
          termYr = 2028, surveyInx = 4)

compDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
              scenario = "constGrowth2001OMandEM_RandRecHCR1",
              termYr = 2028, surveyInx = 4)

recrDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
              scenario = "constGrowth2001OMandEM_RandRecHCR1", termYr = 2028)

catchDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
              scenario = "constGrowth2001OMandEM_RandRecHCR1", termYr = 2028)

FmsyDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
              scenario = "constGrowth2001OMandEM_RandRecHCR1", termYr = 2028)

age1plusDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
              scenario = "constGrowth2001OMandEM_RandRecHCR1", termYr = 2028)
```

## Self test of constant growth and selectivity as OM and EM with moderate data quality starting 2005 applying EM
```{r constGrowth2005OMandEM_RandRecEM}
bDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
          scenario = "constGrowth2005OMandEM_RandRecEM",
          termYr = 2028, surveyInx = 4)

compDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
              scenario = "constGrowth2005OMandEM_RandRecEM",
              termYr = 2028, surveyInx = 4)

recrDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
              scenario = "constGrowth2005OMandEM_RandRecEM", termYr = 2028)

catchDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
              scenario = "constGrowth2005OMandEM_RandRecEM", termYr = 2028)

FmsyDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
              scenario = "constGrowth2005OMandEM_RandRecEM", termYr = 2028)

age1plusDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
              scenario = "constGrowth2005OMandEM_RandRecEM", termYr = 2028)
```

## Constant growth and selectivity in 2001 for OM and 2005 for EM with moderate data quality applying HCR1
```{r constGrowth2001OM_constGrowth2005EM_RandRecHCR1}
bDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
          scenario = "constGrowth2001OM_constGrowth2005EM_RandRecHCR1",
          termYr = 2028, surveyInx = 4)

compDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
              scenario = "constGrowth2001OM_constGrowth2005EM_RandRecHCR1",
              termYr = 2028, surveyInx = 4)

recrDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
              scenario = "constGrowth2001OM_constGrowth2005EM_RandRecHCR1", termYr = 2028)

catchDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
              scenario = "constGrowth2001OM_constGrowth2005EM_RandRecHCR1", termYr = 2028)

FmsyDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
              scenario = "constGrowth2001OM_constGrowth2005EM_RandRecHCR1", termYr = 2028)

age1plusDiagPlots(dir = "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios",
              scenario = "constGrowth2001OM_constGrowth2005EM_RandRecHCR1", termYr = 2028)

# try fit to mean comp length metric from r4ss
```