---
title: "SardineMSE_SupplInfo"
author: "Robert Wildermuth"
date: "11/4/2022"
output: pdf_document
---
# Evaluating robustness of harvest control rules to climate-driven variability in Pacific sardine recruitment
Robert P. Wildermuth^1,2^, Desiree Tommasi^1,2^, Peter Kuriyama^2^, James Smith^1,2^, and Isaac Kaplan^3^
^1^ University of California, Santa Cruz, Institute of Marine Sciences’ Fisheries Collaborative Program, 1156 High Street, Santa Cruz, California 95064, U.S.A.
^2^ Fisheries Research Division, Southwest Fisheries Science Center, National Marine Fisheries Service, National Oceanic and Atmospheric Administration, 8901 La Jolla Shores Drive, La Jolla, California 92037, U.S.A.
^3^ Conservation Biology Division, Northwest Fisheries Science Center, National Marine Fisheries Service, National Oceanic and Atmospheric Administration, 2725 Montlake Boulevard, East Seattle, Washington 98112, U.S.A.

**Supplementary Information: Tables and Figures**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(r4ss)
library(tidyverse)
library(RColorBrewer)
library(scales)
library(gridExtra)

source("../SardineMSE/R/CalcPerformance.R")
source("../SardineMSE/R/CalcTermTS.R")

memory.limit(size = 30000)

# Read in data and calculate metrics --------------------------------------

mseDir <- "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios"
termYr <- 2068

smryOutputList <- readRDS(file.path(mseDir, 
                                    "serverRegARPDOcyclPDOclimSSTMICE_allHCRs_addlResults.RDS"))

performanceList <- CalcPerformance(smryOutputList)

metricsTbl <- performanceList$perfomanceMetrics

omName <- grep("_OM", smryOutputList$tsSmry$model_run,
               fixed = TRUE, value = TRUE)[1]

ageComp <- smryOutputList$ageComp %>% filter(Yr > 2019) 

# Clear up some memory
smryOutputList$lenComp <- NULL
smryOutputList$ageComp <- NULL
```

```{r, ageComp, echo=FALSE, warning=FALSE}
ageComp <- ageComp %>% filter(model_run == omName) %>% 
              mutate(nameHCR = case_when(HCR == "HCR0" ~ "NoCat",
                                         HCR == "HCR1" ~ "PFMCF018",
                                         HCR == "HCR2" ~ "PFMCFSST",
                                         HCR == "HCR3" ~ "ConstF",
                                         HCR == "HCR5" ~ "Pikitch",
                                         HCR == "HCR6" ~ "40-10",
                                         HCR == "HCR7" ~ "DynPik",
                                         HCR == "HCR8" ~ "Dyn40-10",
                                         HCR == "HCR9" ~ "Index"))
ageComp <- ageComp %>% select("Fleet", "Fleet_Name", "Yr", "Seas", "All_exp_mean",
                              "model_run", "iteration", "scenario", "HCR", 
                              "nameHCR", "recScen")
popAgeComp <- ageComp %>% filter(recScen %in% c("ARRec", "PDOclimRec",
                                                "PDOcyclRec", "MICERec")) %>%
                mutate(Surv_OR_Fleet = case_when(Fleet == 4 ~ "Survey",
                                                 Fleet != 4 ~ "Catch")) %>%
                group_by(Surv_OR_Fleet, nameHCR) %>%
                summarize(meanAge = mean(All_exp_mean),
                          medMeanAge = median(All_exp_mean),
                          hi95MeanAge = quantile(All_exp_mean, probs = 0.95),
                          low05MeanAge = quantile(All_exp_mean, probs = 0.05))


```

## Operating model behavior

## Estimation model fit

## Performance metrics by scenario

Biomass and Catch metrics

```{r}
age1PlusBio <- smryOutputList$tsSmry %>% filter(year > 2019, Seas == 1,
                                                model_run == omName) %>% 
                mutate(HCR = sub(pattern = ".*Rec","", scenario),
                       recScen = sub(pattern = "HCR.*","", scenario)) %>%
                mutate(recScen = sub(pattern = ".*EM_","", recScen),
                       nameHCR = case_when(HCR == "HCR0" ~ "NoCat",
                                           HCR == "HCR1" ~ "PFMCF018",
                                           HCR == "HCR2" ~ "PFMCFSST",
                                           HCR == "HCR3" ~ "ConstF",
                                           HCR == "HCR5" ~ "Pikitch",
                                           HCR == "HCR6" ~ "40-10",
                                           HCR == "HCR7" ~ "DynPik",
                                           HCR == "HCR8" ~ "Dyn40-10",
                                           HCR == "HCR9" ~ "Index")) %>%
                select(Bio_smry, year, model_run, iteration, scenario, 
                       HCR, recScen, nameHCR)

ssbBio <- smryOutputList$dqSmry %>% filter(year > 2019, year < 2070,
                                           model_run == omName) %>% 
                mutate(HCR = sub(pattern = ".*Rec","", scenario),
                       recScen = sub(pattern = "HCR.*","", scenario)) %>%
                mutate(recScen = sub(pattern = ".*EM_","", recScen),
                       nameHCR = case_when(HCR == "HCR0" ~ "NoCat",
                                           HCR == "HCR1" ~ "PFMCF018",
                                           HCR == "HCR2" ~ "PFMCFSST",
                                           HCR == "HCR3" ~ "ConstF",
                                           HCR == "HCR5" ~ "Pikitch",
                                           HCR == "HCR6" ~ "40-10",
                                           HCR == "HCR7" ~ "DynPik",
                                           HCR == "HCR8" ~ "Dyn40-10",
                                           HCR == "HCR9" ~ "Index")) %>%
                select(Value.SSB, year, model_run, iteration, scenario, 
                       HCR, recScen, nameHCR)

totCatch <- smryOutputList$tsSmry %>% filter(year > 2019, 
                                             model_run == omName) %>% 
                mutate(totCatch = retainB_1 + retainB_2 + retainB_3) %>%
                group_by(year, model_run, iteration, scenario) %>%
                # summarize total catch within year
                dplyr::summarize(totCatch = sum(totCatch)) %>%
                mutate(HCR = sub(pattern = ".*Rec","", scenario),
                       recScen = sub(pattern = "HCR.*","", scenario)) %>%
                mutate(recScen = sub(pattern = ".*EM_","", recScen),
                       nameHCR = case_when(HCR == "HCR0" ~ "NoCat",
                                           HCR == "HCR1" ~ "PFMCF018",
                                           HCR == "HCR2" ~ "PFMCFSST",
                                           HCR == "HCR3" ~ "ConstF",
                                           HCR == "HCR5" ~ "Pikitch",
                                           HCR == "HCR6" ~ "40-10",
                                           HCR == "HCR7" ~ "DynPik",
                                           HCR == "HCR8" ~ "Dyn40-10",
                                           HCR == "HCR9" ~ "Index"),
                       posTotCatch = case_when(totCatch == 0 ~ NA_real_, # to summarize non-zero catch stats
                                               TRUE ~ totCatch)) %>%
                select(totCatch, posTotCatch, year, model_run, iteration,  
                       scenario, HCR, recScen, nameHCR)

bioCat <- age1PlusBio %>% full_join(y = ssbBio, 
                                    by = c("year", "model_run", 
                                           "iteration", "scenario", 
                                           "HCR", "recScen", "nameHCR")) %>% 
            full_join(y = totCatch, by = c("year", "model_run", 
                                           "iteration", "scenario", 
                                           "HCR", "recScen", "nameHCR")) %>%
            pivot_longer(cols = c(totCatch, posTotCatch, Value.SSB, Bio_smry),
                         names_to = "Metric",
                         values_to = "biomass_mt") %>%
            filter(recScen %in% c("ARRec", "PDOclimRec",
                                  "PDOcyclRec", "MICERec")) %>%
            group_by(Metric, nameHCR) %>%
            summarize(mean = mean(biomass_mt, na.rm = TRUE),
                      median = median(biomass_mt, na.rm = TRUE),
                      hi95 = quantile(biomass_mt, probs = 0.95, na.rm = TRUE),
                      low05 = quantile(biomass_mt, probs = 0.05, na.rm = TRUE),
                      sd = sd(biomass_mt, na.rm = TRUE))

```

### Additional metrics from Hurtado-Ferro and Punt 2014
Calculate zero catch and catch below 50Kt metrics from Hurtado-Ferro and Punt 2014
```{r}

lowCatCount <- totCatch %>%
                mutate(zeroCat = totCatch == 0,
                       lowCat = totCatch < 50000) %>%
                group_by(model_run, iteration, scenario, HCR, recScen, nameHCR) %>%
                mutate(zeroCatLength = sequence(rle(zeroCat)$lengths),
                       lowCatLength = sequence(rle(lowCat)$lengths))
  
lowCatFreq <- lowCatCount %>% group_by(model_run, iteration, scenario, HCR, 
                                       recScen, nameHCR) %>%
                summarize(yrsN = n(),
                          zeroCatFreq = sum(zeroCat)/yrsN,
                          lowCatFreq = sum(lowCat)/yrsN)
  
zeroCatLen <- lowCatCount %>% group_by(model_run, iteration, scenario, zeroCat, 
                                       HCR, recScen, nameHCR) %>%
                summarize(zeroCatLenMax = max(zeroCatLength)) %>%
                filter(zeroCat == TRUE)
lowCatLen <- lowCatCount %>% group_by(model_run, iteration, scenario, lowCat, 
                                      HCR, recScen, nameHCR) %>%
                summarize(lowCatLenMax = max(lowCatLength)) %>%
                filter(lowCat == TRUE)

lowCatFreq %>% full_join(y = zeroCatLen, 
                                    by = c("model_run", "iteration", "scenario", 
                                           "HCR", "recScen", "nameHCR")) %>% 
            full_join(y = lowCatLen, by = c("model_run", "iteration", "scenario", 
                                           "HCR", "recScen", "nameHCR")) %>%
            pivot_longer(cols = c(zeroCatFreq, lowCatFreq, zeroCatLenMax, lowCatLenMax),
                         names_to = "Metric",
                         values_to = "value") %>%
            filter(recScen %in% c("ARRec", "PDOclimRec",
                                  "PDOcyclRec", "MICERec")) %>%
            group_by(Metric, nameHCR) %>%
            summarize(mean = mean(value, na.rm = TRUE),
                      median = median(value, na.rm = TRUE),
                      hi95 = quantile(value, probs = 0.95, na.rm = TRUE),
                      low05 = quantile(value, probs = 0.05, na.rm = TRUE))
```

### Comparison of PFMC control rules by scenario
```{r}
# Compare performance of HCR2 among scenarios -----------------------------

annualRelBioCat %>% filter(HCR %in% c("HCR1", "HCR2")) %>%
  pivot_longer(cols = c(relAnnBioMax, relAnnCatMax), names_to = "Metric",
               values_to = "relAnn") %>%
  group_by(recScen, HCR, Metric) %>%
  summarize(meanRel = mean(relAnn),
            medRel = median(relAnn),
            hiRel = quantile(relAnn, probs = 0.975),
            loRel = quantile(relAnn, probs = 0.025),
            q1Rel = quantile(relAnn, probs = 0.25),
            q3Rel = quantile(relAnn, probs = 0.75),
            nRel = n()) %>% 
  ggplot(aes(x = recScen, fill = HCR)) +
  geom_boxplot(aes(ymin = loRel, lower = q1Rel, middle = medRel, 
                   upper = q3Rel, ymax = hiRel),
               stat = "identity") +
  theme_minimal() +
  facet_wrap(~Metric, scales = "free") +
  scale_fill_manual(values = hcrPal[2:3], labels = hcrLabels[2:3]) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
  # labs(y = "Annual Age1+ Biomass:Max in Poor Recruitment Iters", x = "HCR")

rebuildTime %>% filter(HCR %in% c("HCR1", "HCR2")) %>% 
  pivot_longer(cols = c(nClosures, meanRebuildTime, medRebuildTime), 
               names_to = "Metric", values_to = "value") %>%
  group_by(recScen, HCR, Metric) %>%
  summarize(meanRebuild = mean(value),
            medRebuild = median(value),
            hiRebuild = quantile(value, probs = 0.975),
            loRebuild = quantile(value, probs = 0.025),
            q1Rebuild = quantile(value, probs = 0.25),
            q3Rebuild = quantile(value, probs = 0.75),
            nRebuild = n()) %>% 
  ggplot(aes(x = recScen, fill = HCR)) +
  geom_boxplot(aes(ymin = loRebuild, lower = q1Rebuild, middle = medRebuild, 
                   upper = q3Rebuild, ymax = hiRebuild),
               stat = "identity") +
  theme_minimal() +
  facet_wrap(~Metric, scales = "free") +
  scale_fill_manual(values = hcrPal[2:3], labels = hcrLabels[2:3]) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

metricsTbl %>% filter(HCR %in% c("HCR1", "HCR2")) %>% 
  pivot_longer(cols = c(closuresFreq, collapseFreq, bonanzaFreq, 
                        meanCollapseSever, rebuildLengthMax), 
               names_to = "Metric", values_to = "value") %>%
  group_by(recScen, HCR, Metric) %>%
  summarize(meanRebuild = mean(value),
            medRebuild = median(value),
            hiRebuild = quantile(value, probs = 0.975),
            loRebuild = quantile(value, probs = 0.025),
            q1Rebuild = quantile(value, probs = 0.25),
            q3Rebuild = quantile(value, probs = 0.75),
            nRebuild = n()) %>% 
  ggplot(aes(x = recScen, fill = HCR)) +
  geom_boxplot(aes(ymin = loRebuild, lower = q1Rebuild, middle = medRebuild, 
                   upper = q3Rebuild, ymax = hiRebuild),
               stat = "identity") +
  theme_minimal() +
  facet_wrap(~Metric, scales = "free") +
  scale_fill_manual(values = hcrPal[2:3], labels = hcrLabels[2:3]) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

## Confusion tables