---
title: "SardineMSE_SupplInfo"
author: "Robert Wildermuth"
date: "11/4/2022"
output: pdf_document
---
# Evaluating robustness of harvest control rules to climate-driven variability in Pacific sardine recruitment
Robert P. Wildermuth^1,2^, Desiree Tommasi^1,2^, Peter Kuriyama^2^, James Smith^1,2^, and Isaac Kaplan^3^
^1^ University of California, Santa Cruz, Institute of Marine Sciences’ Fisheries Collaborative Program, 1156 High Street, Santa Cruz, California 95064, U.S.A.
^2^ Fisheries Research Division, Southwest Fisheries Science Center, National Marine Fisheries Service, National Oceanic and Atmospheric Administration, 8901 La Jolla Shores Drive, La Jolla, California 92037, U.S.A.
^3^ Conservation Biology Division, Northwest Fisheries Science Center, National Marine Fisheries Service, National Oceanic and Atmospheric Administration, 2725 Montlake Boulevard, East Seattle, Washington 98112, U.S.A.

**Supplementary Information: Tables and Figures**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, warning=FALSE}
library(r4ss)
library(tidyverse)
library(RColorBrewer)
library(scales)
library(gridExtra)

localPath <- "C:/Users/r.wildermuth/Documents/FutureSeas"

source(file.path(localPath, "SardineMSE/R/CalcPerformance.R"))
source(file.path(localPath, "SardineMSE/R/CalcTermTS.R"))

memory.limit(size = 30000)

# Read in data and calculate metrics --------------------------------------

mseDir <- file.path(localPath, "SardineScenarios")
termYr <- 2068

smryOutputList <- readRDS(file.path(mseDir, 
                                    "serverRegARPDOcyclPDOclimSSTMICE_allHCRs_Results.RDS"))

performanceList <- CalcPerformance(smryOutputList)

metricsTbl <- performanceList$perfomanceMetrics %>% 
                  mutate(nameHCR = case_when(HCR == "HCR0" ~ "NoCat",
                                             HCR == "HCR1" ~ "PFMCF018",
                                             HCR == "HCR2" ~ "PFMCFSST",
                                             HCR == "HCR3" ~ "ConstF",
                                             HCR == "HCR5" ~ "Pikitch",
                                             HCR == "HCR6" ~ "40-10",
                                             HCR == "HCR7" ~ "DynPik",
                                             HCR == "HCR8" ~ "Dyn40-10",
                                             HCR == "HCR9" ~ "Index"))

omName <- grep("_OM", smryOutputList$tsSmry$model_run,
               fixed = TRUE, value = TRUE)[1]

ageComp <- smryOutputList$ageComp %>% filter(Yr > 2019) 

# Clear up some memory
smryOutputList$lenComp <- NULL
smryOutputList$ageComp <- NULL

# Prep for plotting
omName <- grep("_OM", smryOutputList$tsSmry$model_run,
               fixed = TRUE, value = TRUE)[1]
hcrPal <- brewer.pal(11, "Set3")[-2]

hcrLabels <- c("NoCat", "PFMCF018", "PFMCFSST", "ConstF", "Pikitch", "40-10",
               "DynPik", "Dyn40-10", "Index")

# define reference scenarios to use in plot calculations
refScens <- c("ARRec", "PDOcyclRec", "MICERec", "PDOclimRec")

# get terminal estimates of these values for timeseries plots
termTS <- CalcTermTS(smryOutputList, termYr = termYr) %>%
            mutate(nameHCR = case_when(HCR == "HCR0" ~ "NoCat",
                                       HCR == "HCR1" ~ "PFMCF018",
                                       HCR == "HCR2" ~ "PFMCFSST",
                                       HCR == "HCR3" ~ "ConstF",
                                       HCR == "HCR5" ~ "Pikitch",
                                       HCR == "HCR6" ~ "40-10",
                                       HCR == "HCR7" ~ "DynPik",
                                       HCR == "HCR8" ~ "Dyn40-10",
                                       HCR == "HCR9" ~ "Index"),
                   recScen = factor(recScen, levels = c("ARRec", "PDOcyclRec", 
                                                        "MICERec", "PDOclimRec",
                                                        "RegRec", "SSTRec")))
```

```{r, ageComp, echo=FALSE, warning=FALSE}
ageComp <- ageComp %>% filter(model_run == omName) %>% 
              mutate(nameHCR = case_when(HCR == "HCR0" ~ "NoCat",
                                         HCR == "HCR1" ~ "PFMCF018",
                                         HCR == "HCR2" ~ "PFMCFSST",
                                         HCR == "HCR3" ~ "ConstF",
                                         HCR == "HCR5" ~ "Pikitch",
                                         HCR == "HCR6" ~ "40-10",
                                         HCR == "HCR7" ~ "DynPik",
                                         HCR == "HCR8" ~ "Dyn40-10",
                                         HCR == "HCR9" ~ "Index"))
ageComp <- ageComp %>% select("Fleet", "Fleet_Name", "Yr", "Seas", "All_exp_mean",
                              "model_run", "iteration", "scenario", "HCR", 
                              "nameHCR", "recScen")
popAgeComp <- ageComp %>% filter(recScen %in% c("ARRec", "PDOclimRec",
                                                "PDOcyclRec", "MICERec")) %>%
                mutate(Surv_OR_Fleet = case_when(Fleet == 4 ~ "Survey",
                                                 Fleet != 4 ~ "Catch")) %>%
                group_by(Surv_OR_Fleet, nameHCR) %>%
                summarize(meanAge = mean(All_exp_mean),
                          medMeanAge = median(All_exp_mean),
                          hi95MeanAge = quantile(All_exp_mean, probs = 0.95),
                          low05MeanAge = quantile(All_exp_mean, probs = 0.05))


```

## Operating model behavior

### Stock Synthesis model parameterization

- Fit of OM to historical acoustic-trawl index and comparison of age 1+ biomass timeseries by season with Kuriyama et al. 2020 assessment. 

```{r, kuriyamaFit, echo=FALSE, warning=FALSE}
# read in 2020 assessment files and plot fit
assessment2020 <- read_csv(file.path(localPath, "SardineMSE/dat/Kuriyamaetal2020_SmryBiobasemodel.csv")) %>%
                    mutate(model = "2020assessment") 

mseOM <- SS_output(file.path(localPath,
                             "SardineMSE/scenarioModels/start2001/constGrowthMidSteepNewSelex_OM"),
                   verbose = FALSE, printstats = FALSE)
SSplotIndices(mseOM, subplots = 2, fleets = 4)

mseOM$timeseries %>% select(Yr, Seas, Bio_smry) %>%
  mutate(model = "OM") %>%
  rbind(assessment2020) %>%
  ggplot(aes(x = Yr, y = Bio_smry, col = model)) +
  geom_line() +
  facet_wrap(~Seas)
```

Table of model parameters for OM and EM Stock Synthesis models, including phase estimation settings for the EM.

```{r, ssParsTbl, echo=FALSE, warning=FALSE}
parsOM <- mseOM$parameters %>% select(Label, Value)

mseEM <- SS_output(file.path(localPath,
                             "SardineMSE/scenarioModels/start2005/constGrowthMidSteepNewSelex_EM"),
                   verbose = FALSE, printstats = FALSE)
parsEM <- mseEM$parameters %>% select(Label, Value, Phase)

full_join(parsOM, parsEM, by = "Label") %>% 
  rename(OM_Value = Value.x,
         EM_Value = Value.y,
         EM_Phase = Phase)
```

###Timeseries of derived quantities for each scenario
Biomass
```{r, bioSeries, echo=FALSE, warning=FALSE}
 # timeseries plot for presentation
sampleDat <- termTS %>% filter(model_run == omName, HCR == "HCR0") %>%
  select(Bio_smry, totCatch, year, model_run, iteration, scenario, HCR, recScen) %>%
  group_by(year, scenario, HCR, recScen) %>%
  summarize(meanAge1Plus = mean(Bio_smry),
            medAge1Plus = median(Bio_smry),
            lowAge1Plus = quantile(Bio_smry, probs = 0.05, na.rm = TRUE),
            hiAge1Plus = quantile(Bio_smry, probs = 0.95, na.rm = TRUE),
            meanCatch = mean(totCatch),
            medCatch = median(totCatch),
            lowCatch = quantile(totCatch, probs = 0.05, na.rm = TRUE),
            hiCatch = quantile(totCatch, probs = 0.95, na.rm = TRUE))
            
termTS %>% filter(model_run == omName, HCR == "HCR0") %>%
  ggplot(aes(x = year, y = Bio_smry)) +
  geom_vline(xintercept = 2019, color = "gray", linetype = "dashed") +
  geom_line(aes(linetype = as.character(iteration)), color = "grey",alpha = 0.4) +
  # geom_ribbon(aes(ymin = lowAge1Plus, ymax = hiAge1Plus, alpha = 0.3)) +
  facet_grid(rows = vars(HCR), cols = vars(recScen)) +
  theme_classic() +
  labs(x = NULL, y = "Age 1+ Biomass (mt)",
  caption = "Median (solid line), 80% CI (grey shaded ribbon) under a No Catch (HCR0) management rule\n for each recruitment scenario.") +
  scale_linetype_manual(values = rep("solid", 500)) +
  # scale_color_manual(values = brewer.pal(n = 5, "Pastel1")) +
  geom_line(data = sampleDat, aes(x = year, y = medAge1Plus)) +
  theme(legend.position = "none",
        plot.caption = element_text(hjust = 0),
        plot.caption.position = "plot",
        strip.text.y = element_blank(),
        panel.grid = element_blank()) +
  geom_hline(yintercept = 150000, color = "red") +
  coord_cartesian(ylim = c(0, 2e7))

errCompare <- CalcRelErr(smryOutputList = smryOutputList,
                         termTS = termTS,
                         termYr = termYr)
```
 
Recruitment
```{r, recSeries, echo=FALSE, warning=FALSE}
itSamp <- sample(unique(termTS$iteration), size = 3)

termTS %>% filter(model_run == omName,
                  HCR == "HCR0", iteration %in% itSamp) %>%
  ggplot(aes(x = year, y = rec_dev)) +
  geom_line(aes(linetype = as.character(iteration), 
                color = as.character(iteration))) + 
  scale_linetype_manual(values = rep("solid", 50)) +
  # scale_color_manual(values = brewer.pal(n = 5, "Pastel1")) +
  guides(linetype = "none") +
  geom_hline(yintercept = 0, color = "grey") +
  facet_grid(rows = vars(iteration), cols = vars(recScen)) + 
  theme_classic() +
  geom_vline(xintercept = 2019, color = "gray", linetype = "dashed") +
  labs(x = "Year", y = "Recruitment Deviation") +
  theme(legend.position = "none",
        plot.caption = element_text(hjust = 0),
        plot.caption.position = "plot",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        strip.text.y = element_blank())
```
 
Catch
```{r, catSeries, echo=FALSE, warning=FALSE}
 termTS %>% filter(model_run == omName) %>%
  ggplot(aes(x = year, y = totCatch)) +
  geom_vline(xintercept = 2019, color = "gray", linetype = "dashed") +
  geom_line(aes(linetype = as.character(iteration)), color = "grey",alpha = 0.4) +
  # geom_ribbon(aes(ymin = lowCatch, ymax = hiCatch, alpha = 0.3)) +
  facet_grid(rows = vars(nameHCR), cols = vars(recScen)) +
  theme_classic() +
  labs(x = NULL, y = "Catch (mt)",
  caption = "Median (solid line), 80% CI (grey shaded ribbon) under each management rule\n for each recruitment scenario.") +
  scale_linetype_manual(values = rep("solid", 500)) +
  # scale_color_manual(values = brewer.pal(n = 5, "Pastel1")) +
  geom_line(data = sampleDat, aes(x = year, y = medCatch)) +
  theme(legend.position = "none",
        plot.caption = element_text(hjust = 0),
        plot.caption.position = "plot",
        strip.text.y = element_blank(),
        panel.grid = element_blank()) +
  geom_hline(yintercept = 200000, color = "red") +
  coord_cartesian(ylim = c(0, 210000))
```
 
Unfished biomass (B0)
```{r, B0Series, echo=FALSE, warning=FALSE}
# Look at timeseries of B0 and account for non-convergence
smryOutputList$sclSmry %>% mutate(emYear = as.numeric(regmatches(model_run,
                                                        gregexpr("[[:digit:]]+", 
                                                                 model_run))))  %>%
  filter(model_run != omName, HCR != "HCR0", max_grad < 0.01, 
         iteration == sample(1:max(unique(termTS$iteration)), size = 10)) %>%
  ggplot(aes(x = emYear, y = log(SSB_Unfished))) +
  geom_line(ggplot2::aes(linetype = as.character(iteration), color = HCR))+
    #ggplot2::scale_color_manual(values = c("#D65F00", "blue")) +
    ggplot2::scale_linetype_manual(values = rep("solid", 100)) +
  ggplot2::guides(linetype = "none") +
    ggplot2::facet_grid(rows = vars(nameHCR), cols = vars(recScen)) +
    ggplot2::theme_classic() + 
  #geom_rug(data = convrgCheck, mapping = aes(x = emYear),
  #                     sides = "b", inherit.aes = FALSE) +
  labs(x = "Year", y = "B0 (Unfished SSB)",
       caption = "Sample of estimated unfished SSB (B0) in the assessment under each management rule (rows) and each recruitment\n scenario (columns).") +
  theme(legend.position = "none",
        plot.caption = element_text(hjust = 0),
        plot.caption.position = "plot")
```

## Estimation model fit
We provide diagnostics for the fit of the EM in three iterations for the autocorrelated recruitment scenario and SST-based HCR application. 

Time series of OM and terminal EM estimate of age 1+ biomass with simulated data
```{r, exAge1PlusFit}
termTS %>% filter(iteration %in% itSamp) %>%
  ggplot(aes(x = Yr, y = Bio_Smry.1)) +
    ggplot2::geom_vline(xintercept = 2019, color = "gray") +
    ggplot2::geom_line(ggplot2::aes(linetype = as.character(iteration), color = model_run))+
    ggplot2::scale_color_manual(values = c("#D65F00", "blue")) +
    ggplot2::scale_linetype_manual(values = rep("solid", 50)) +
    ggplot2::guides(linetype = "none") +
    ggplot2::facet_wrap(. ~ iteration) +
    ggplot2::theme_classic()
```

Time series of OM and terminal EM estimate of recruitment and recruitment deviations
```{r, exRecFit}
termTS %>% filter(iteration %in% itSamp) %>%
  ggplot(aes(x = year, y = Value.Recr)) +
    ggplot2::geom_vline(xintercept = 2019, color = "gray") +
    ggplot2::geom_line(ggplot2::aes(linetype = as.character(iteration), color = model_run))+
    ggplot2::scale_color_manual(values = c("#D65F00", "black", "blue")) +
    ggplot2::scale_linetype_manual(values = rep("solid", 50)) +
    ggplot2::guides(linetype = "none") +
    ggplot2::facet_wrap(. ~ iteration) +
    ggplot2::theme_classic()
```

Histograms of age composition
```{r, compCompare}
ageComp %>% filter(iteration %in% itSamp) %>%
  ggplot() +
  geom_hist() +
  facet_grid(rows = iteration, cols = model_run)
```

Evolution of relative error in age 1+ biomass, including survey index, and recruitment deviations
```{r, exREseries}
# biomass error
errCompare %>% filter(iteration %in% itSamp) %>%
  ggplot(aes(x = Yr, y = errSmryBio)) +
    ggplot2::geom_vline(xintercept = 2019, color = "gray") +
    geom_hline(yintercept = 0, color = "black") +
    ggplot2::geom_line(ggplot2::aes(linetype = as.character(iteration), color = 2))+
    #ggplot2::scale_color_manual(values = c("#D65F00", "black", rep("blue", 5))) +
    ggplot2::scale_linetype_manual(values = rep("solid", 50)) +
    ggplot2::guides(linetype = "none") +
    ggplot2::facet_wrap(. ~ iteration) +
    ggplot2::theme_classic() +
    ylab("Relative Error (Summary Biomass)")

# !!RW: need to workshop recruitment error
```

- Relative error of EM over all assessment years (similar to Fig 5)
```{r, REallyrs}
annualRE <- errCompare %>% filter(year <= emYear.x | plotGroup == "ATsurvey") %>%
  select(age1plusEM, age1plusOM, errSmryBio, year, model_run.x, iteration, scenario, HCR, recScen, plotGroup) %>%
  group_by(year,  scenario, HCR, recScen, plotGroup) %>%#iteration,
  summarize(meanYrRE = mean(errSmryBio),
            medYrRE = median(errSmryBio),
            hiYrRE = quantile(errSmryBio, probs = 0.975),
            loYrRE = quantile(errSmryBio, probs = 0.025),
            q1YrRE = quantile(errSmryBio, probs = 0.25),
            q3YrRE = quantile(errSmryBio, probs = 0.75),
            nErrs = n())

annualRE %>% filter(plotGroup != "non-convrg", HCR == "HCR2",
                    recScen %in% refScens) %>%
  mutate(recScen = factor(recScen, levels = c("ARRec", "MICERec",
                                              "PDOcyclRec", "PDOclimRec",
                                              "RegRec", "SSTRec"))) %>%
  ggplot(aes(x = year, fill = recScen, group = year)) +
  geom_boxplot(aes(ymin = loYrRE, lower = q1YrRE, middle = medYrRE, 
                   upper = q3YrRE, ymax = hiYrRE),
               stat = "identity") +
  facet_wrap(~recScen, ncol = 2) +
  geom_hline(yintercept = 0) +
  theme_classic() +
  scale_fill_manual(values = brewer.pal(6, "Set2")[c(1,3,2,4:6)]) +
  theme(#axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "none") +
  labs(x = "Year", y = "Relative Error (%)") 
```

- Relative error of EM in forecast
```{r, REforecast}
annualRE <- errCompare %>% filter(year == emYear.x + 1 | plotGroup == "ATsurvey") %>%
  select(age1plusEM, age1plusOM, errSmryBio, year, model_run.x, iteration, scenario, HCR, recScen, plotGroup) %>%
  group_by(year,  scenario, HCR, recScen, plotGroup) %>%#iteration,
  summarize(meanYrRE = mean(errSmryBio),
            medYrRE = median(errSmryBio),
            hiYrRE = quantile(errSmryBio, probs = 0.975),
            loYrRE = quantile(errSmryBio, probs = 0.025),
            q1YrRE = quantile(errSmryBio, probs = 0.25),
            q3YrRE = quantile(errSmryBio, probs = 0.75),
            nErrs = n())

annualRE %>% filter(plotGroup != "non-convrg", HCR == "HCR2",
                    recScen %in% refScens) %>%
  mutate(recScen = factor(recScen, levels = c("ARRec", "MICERec",
                                              "PDOcyclRec", "PDOclimRec",
                                              "RegRec", "SSTRec"))) %>%
  ggplot(aes(x = year, fill = recScen, group = year)) +
  geom_boxplot(aes(ymin = loYrRE, lower = q1YrRE, middle = medYrRE, 
                   upper = q3YrRE, ymax = hiYrRE),
               stat = "identity") +
  facet_wrap(~recScen, ncol = 2) +
  geom_hline(yintercept = 0) +
  theme_classic() +
  scale_fill_manual(values = brewer.pal(6, "Set2")[c(1,3,2,4:6)]) +
  theme(#axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "none") +
  labs(x = "Year", y = "Relative Error (%)") 
```

- EM convergence statistics
```{r, cnvrg}
metricsTbl %>% filter(!is.na(frqNonConvg)) %>% 
  group_by(HCR, recScen) %>%
  summarize(maxNonConvrg = max(frqNonConvg, na.rm = TRUE), 
            minNonConvrg = min(frqNonConvg, na.rm = TRUE)) %>%
  print(n = 28)
```

## Performance metrics by scenario

Biomass and Catch metrics

```{r}
age1PlusBio <- smryOutputList$tsSmry %>% filter(year > 2019, Seas == 1,
                                                model_run == omName) %>% 
                mutate(HCR = sub(pattern = ".*Rec","", scenario),
                       recScen = sub(pattern = "HCR.*","", scenario)) %>%
                mutate(recScen = sub(pattern = ".*EM_","", recScen),
                       nameHCR = case_when(HCR == "HCR0" ~ "NoCat",
                                           HCR == "HCR1" ~ "PFMCF018",
                                           HCR == "HCR2" ~ "PFMCFSST",
                                           HCR == "HCR3" ~ "ConstF",
                                           HCR == "HCR5" ~ "Pikitch",
                                           HCR == "HCR6" ~ "40-10",
                                           HCR == "HCR7" ~ "DynPik",
                                           HCR == "HCR8" ~ "Dyn40-10",
                                           HCR == "HCR9" ~ "Index")) %>%
                select(Bio_smry, year, model_run, iteration, scenario, 
                       HCR, recScen, nameHCR)

ssbBio <- smryOutputList$dqSmry %>% filter(year > 2019, year < 2070,
                                           model_run == omName) %>% 
                mutate(HCR = sub(pattern = ".*Rec","", scenario),
                       recScen = sub(pattern = "HCR.*","", scenario)) %>%
                mutate(recScen = sub(pattern = ".*EM_","", recScen),
                       nameHCR = case_when(HCR == "HCR0" ~ "NoCat",
                                           HCR == "HCR1" ~ "PFMCF018",
                                           HCR == "HCR2" ~ "PFMCFSST",
                                           HCR == "HCR3" ~ "ConstF",
                                           HCR == "HCR5" ~ "Pikitch",
                                           HCR == "HCR6" ~ "40-10",
                                           HCR == "HCR7" ~ "DynPik",
                                           HCR == "HCR8" ~ "Dyn40-10",
                                           HCR == "HCR9" ~ "Index")) %>%
                select(Value.SSB, year, model_run, iteration, scenario, 
                       HCR, recScen, nameHCR)

totCatch <- smryOutputList$tsSmry %>% filter(year > 2019, 
                                             model_run == omName) %>% 
                mutate(totCatch = retainB_1 + retainB_2 + retainB_3) %>%
                group_by(year, model_run, iteration, scenario) %>%
                # summarize total catch within year
                dplyr::summarize(totCatch = sum(totCatch)) %>%
                mutate(HCR = sub(pattern = ".*Rec","", scenario),
                       recScen = sub(pattern = "HCR.*","", scenario)) %>%
                mutate(recScen = sub(pattern = ".*EM_","", recScen),
                       nameHCR = case_when(HCR == "HCR0" ~ "NoCat",
                                           HCR == "HCR1" ~ "PFMCF018",
                                           HCR == "HCR2" ~ "PFMCFSST",
                                           HCR == "HCR3" ~ "ConstF",
                                           HCR == "HCR5" ~ "Pikitch",
                                           HCR == "HCR6" ~ "40-10",
                                           HCR == "HCR7" ~ "DynPik",
                                           HCR == "HCR8" ~ "Dyn40-10",
                                           HCR == "HCR9" ~ "Index"),
                       posTotCatch = case_when(totCatch == 0 ~ NA_real_, # to summarize non-zero catch stats
                                               TRUE ~ totCatch)) %>%
                select(totCatch, posTotCatch, year, model_run, iteration,  
                       scenario, HCR, recScen, nameHCR)

bioCat <- age1PlusBio %>% full_join(y = ssbBio, 
                                    by = c("year", "model_run", 
                                           "iteration", "scenario", 
                                           "HCR", "recScen", "nameHCR")) %>% 
            full_join(y = totCatch, by = c("year", "model_run", 
                                           "iteration", "scenario", 
                                           "HCR", "recScen", "nameHCR")) %>%
            pivot_longer(cols = c(totCatch, posTotCatch, Value.SSB, Bio_smry),
                         names_to = "Metric",
                         values_to = "biomass_mt") %>%
            filter(recScen %in% c("ARRec", "PDOclimRec",
                                  "PDOcyclRec", "MICERec")) %>%
            group_by(Metric, nameHCR) %>%
            summarize(mean = mean(biomass_mt, na.rm = TRUE),
                      median = median(biomass_mt, na.rm = TRUE),
                      hi95 = quantile(biomass_mt, probs = 0.95, na.rm = TRUE),
                      low05 = quantile(biomass_mt, probs = 0.05, na.rm = TRUE),
                      sd = sd(biomass_mt, na.rm = TRUE))

```

- Tradeoff plot
```{r, bioCatTradeoff}
termTS %>% filter(model_run == omName, year > 2019) %>%
  ggplot(aes(x = log(Bio_smry), y = log(totCatch), color = HCR)) +
  geom_point() +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_color_manual(values = hcrPal, labels = hcrLabels) +
  labs(y = "Catch (log-mt)", x = "Age1+ Biomass (log-mt)",
       title = "Annual Biomass x Annual Catch",
       caption = "Interaction between annual log-catch and annual log-Age1+ biomass under each HCR (colored points) in each recruitment scenario.") +
  theme(plot.caption = element_text(hjust = 0),
        plot.caption.position = "plot") 
```

Other metrics
```{r}
# Calculate rebuilding
rebuildTime <- CalcRebuildTime(tsSmry = performanceList$tsSmry) %>% 
                  mutate(nameHCR = case_when(HCR == "HCR0" ~ "NoCat",
                                             HCR == "HCR1" ~ "PFMCF018",
                                             HCR == "HCR2" ~ "PFMCFSST",
                                             HCR == "HCR3" ~ "ConstF",
                                             HCR == "HCR5" ~ "Pikitch",
                                             HCR == "HCR6" ~ "40-10",
                                             HCR == "HCR7" ~ "DynPik",
                                             HCR == "HCR8" ~ "Dyn40-10",
                                             HCR == "HCR9" ~ "Index"))

# calculate frequency of TAC = 0
noCatFreq <- annualRelBioCat %>% mutate(TAC0 = totCatch == 0) %>%
                group_by(model_run, iteration, scenario, HCR, recScen) %>%
                summarize(yrsN = n(),
                          nocatFreq = sum(TAC0)/yrsN)

# join tables for clean faceted plots
metricsTbl <- metricsTbl %>% left_join(y = rebuildTime, 
                                       by = c("iteration", "scenario", "nameHCR",
                                              "model_run", "HCR", "recScen")) %>%
                left_join(y = noCatFreq, 
                          by = c("iteration", "scenario", "yrsN",
                                 "model_run", "HCR", "recScen")) %>%
                # Add grouping variable for non/climate scenarios
                mutate(climGroup = case_when(recScen %in% c("ARRec", "PDOcyclRec", 
                                                            "RegRec") ~ "noClim",
                                             recScen %in% c("MICERec", "PDOclimRec", 
                                                            "SSTRec") ~ "clim"),
                       nameHCR = factor(nameHCR, levels = c("NoCat", "PFMCF018", "PFMCFSST", "ConstF",
                                                            "Index", "Pikitch", "40-10", "DynPik", "Dyn40-10")))


# rebuilding time
# look at how many iterations never rebuilt
performanceList$tsSmry %>% filter(closureLength == 50) %>% group_by(HCR, recScen)%>% summarize(nvrRebuiltN = n())
# only 1 iteration in reference set didn't rebuild (iter 77) except under HCR1

rebuild <- rebuildTime %>% 
  group_by(nameHCR, recScen) %>%
  summarize(meanRebuild = mean(meanRebuildTime),
            medRebuild = median(medRebuildTime),
            hiRebuild = quantile(medRebuildTime, probs = 0.95),
            loRebuild = quantile(medRebuildTime, probs = 0.05),
            q1Rebuild = quantile(medRebuildTime, probs = 0.25),
            q3Rebuild = quantile(medRebuildTime, probs = 0.75),
            nRebuild = n()) %>% 
  ggplot(aes(x = nameHCR, fill = nameHCR)) +
  geom_boxplot(aes(ymin = loRebuild, lower = q1Rebuild, middle = medRebuild, 
                   upper = q3Rebuild, ymax = hiRebuild),
               stat = "identity") +
  # ggplot(aes(x = HCR, y = meanRebuildTime)) +
  # geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  #facet_wrap(~recScen, scales = "free") + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = hcrLabels, name = "HCR") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Mean Rebuilding Time (yrs)", x = "HCR")

rebuildTime %>%  
  ggplot(aes(x = HCR, y = nClosures)) +
  geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  #facet_wrap(~recScen, scales = "free") + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = hcrLabels) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Number of Closures", x = "HCR")

rebuildTime %>%  
  group_by(HCR, recScen) %>%
  summarize(meanNclose = mean(nClosures),
            medNclose = median(nClosures),
            high90 = quantile(nClosures, probs = 0.9))

# collapse severity
metricsTbl %>% 
  group_by(nameHCR, recScen) %>%
  summarize(meanCollSevr = mean(meanCollapseSever),
            medCollSevr = median(meanCollapseSever),
            hiCollSevr = quantile(meanCollapseSever, probs = 0.95),
            loCollSevr = quantile(meanCollapseSever, probs = 0.05),
            q1CollSevr = quantile(meanCollapseSever, probs = 0.25),
            q3CollSevr = quantile(meanCollapseSever, probs = 0.75),
            nCollSevr = n()) %>% 
  ggplot(aes(x = nameHCR, fill = nameHCR)) +
  geom_boxplot(aes(ymin = loCollSevr, lower = q1CollSevr, middle = medCollSevr, 
                   upper = q3CollSevr, ymax = hiCollSevr),
               stat = "identity") +
  # ggplot(aes(x = HCR, y = meanCollapseSever)) +
  # geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  #facet_wrap(~recScen, scales = "free") + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = hcrLabels, name = "HCR") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Collapse severity", x = "HCR")

# Catch variation
metricsTbl %>%  filter(HCR != "HCR0") %>%
  group_by(nameHCR, recScen) %>%
  summarize(meanRelCatSD = mean(sdCatch),
            medRelCatSD = median(sdCatch),
            hiRelCatSD = quantile(sdCatch, probs = 0.95),
            loRelCatSD = quantile(sdCatch, probs = 0.05),
            q1RelCatSD = quantile(sdCatch, probs = 0.25),
            q3RelCatSD = quantile(sdCatch, probs = 0.75),
            nRelCatSD = n()) %>% 
  ggplot(aes(x = nameHCR, fill = nameHCR)) +
  geom_boxplot(aes(ymin = loRelCatSD, lower = q1RelCatSD, middle = medRelCatSD, 
                   upper = q3RelCatSD, ymax = hiRelCatSD),
               stat = "identity") +
  # ggplot(aes(x = HCR, y = sdCatch)) +
  # geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen, scales = "free") +
  theme_minimal() +
  scale_fill_manual(values = hcrPal[-1], labels = hcrLabels[-1], name = "HCR") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Catch SD (mt)", x = "HCR")

# cutoff frequency
metricsTbl %>% 
  group_by(nameHCR, recScen) %>%
  summarize(meanFrqClose = mean(closuresFreq),
            medFrqClose = median(closuresFreq),
            hiFrqClose = quantile(closuresFreq, probs = 0.95),
            loFrqClose = quantile(closuresFreq, probs = 0.05),
            q1FrqClose = quantile(closuresFreq, probs = 0.25),
            q3FrqClose = quantile(closuresFreq, probs = 0.75),
            nFrqClose = n()) %>% 
  ggplot(aes(x = nameHCR, fill = nameHCR)) +
  geom_boxplot(aes(ymin = loFrqClose, lower = q1FrqClose, middle = medFrqClose, 
                   upper = q3FrqClose, ymax = hiFrqClose),
               stat = "identity") +
  # ggplot(aes(x = HCR, y = closuresFreq)) +
  # geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen, scales = "free") +
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = hcrLabels, name = "HCR") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Frequency Bt < 150,000 mt", x = "HCR")

# collapse frequency
metricsTbl %>% 
  group_by(nameHCR, recScen) %>%
  summarize(meanFrqColl = mean(collapseFreq),
            medFrqColl = median(collapseFreq),
            hiFrqColl = quantile(collapseFreq, probs = 0.95),
            loFrqColl = quantile(collapseFreq, probs = 0.05),
            q1FrqColl = quantile(collapseFreq, probs = 0.25),
            q3FrqColl = quantile(collapseFreq, probs = 0.75),
            nFrqColl = n()) %>% 
  ggplot(aes(x = nameHCR, fill = nameHCR)) +
  geom_boxplot(aes(ymin = loFrqColl, lower = q1FrqColl, middle = medFrqColl, 
                   upper = q3FrqColl, ymax = hiFrqColl),
               stat = "identity") +
  # ggplot(aes(x = HCR, y = collapseFreq)) +
  # geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen, scales = "free") +
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = hcrLabels, name = "HCR") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Frequency Bt < 50,000 mt", x = "HCR")

# closure frequency
metricsTbl %>% 
  group_by(nameHCR, recScen) %>%
  summarize(meanFrqClos = mean(noCatFreq),
            medFrqClos = median(noCatFreq),
            hiFrqClos = quantile(noCatFreq, probs = 0.95),
            loFrqClos = quantile(noCatFreq, probs = 0.05),
            q1FrqClos = quantile(noCatFreq, probs = 0.25),
            q3FrqClos = quantile(noCatFreq, probs = 0.75),
            nFrqClos = n()) %>% 
  ggplot(aes(x = nameHCR, fill = nameHCR)) +
  geom_boxplot(aes(ymin = loFrqClos, lower = q1FrqClos, middle = medFrqClos, 
                   upper = q3FrqClos, ymax = hiFrqClos),
               stat = "identity") +
  # ggplot(aes(x = HCR, y = collapseFreq)) +
  # geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen, scales = "free") +
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = hcrLabels, name = "HCR") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Frequency TAC = 0", x = "HCR")
```

### Additional metrics from Hurtado-Ferro and Punt 2014
Calculate zero catch and catch below 50Kt metrics from Hurtado-Ferro and Punt 2014
```{r}

lowCatCount <- totCatch %>%
                mutate(zeroCat = totCatch == 0,
                       lowCat = totCatch < 50000) %>%
                group_by(model_run, iteration, scenario, HCR, recScen, nameHCR) %>%
                mutate(zeroCatLength = sequence(rle(zeroCat)$lengths),
                       lowCatLength = sequence(rle(lowCat)$lengths))
  
lowCatFreq <- lowCatCount %>% group_by(model_run, iteration, scenario, HCR, 
                                       recScen, nameHCR) %>%
                summarize(yrsN = n(),
                          zeroCatFreq = sum(zeroCat)/yrsN,
                          lowCatFreq = sum(lowCat)/yrsN)
  
zeroCatLen <- lowCatCount %>% group_by(model_run, iteration, scenario, zeroCat, 
                                       HCR, recScen, nameHCR) %>%
                summarize(zeroCatLenMax = max(zeroCatLength)) %>%
                filter(zeroCat == TRUE)
lowCatLen <- lowCatCount %>% group_by(model_run, iteration, scenario, lowCat, 
                                      HCR, recScen, nameHCR) %>%
                summarize(lowCatLenMax = max(lowCatLength)) %>%
                filter(lowCat == TRUE)

lowCatFreq %>% full_join(y = zeroCatLen, 
                                    by = c("model_run", "iteration", "scenario", 
                                           "HCR", "recScen", "nameHCR")) %>% 
            full_join(y = lowCatLen, by = c("model_run", "iteration", "scenario", 
                                           "HCR", "recScen", "nameHCR")) %>%
            pivot_longer(cols = c(zeroCatFreq, lowCatFreq, zeroCatLenMax, lowCatLenMax),
                         names_to = "Metric",
                         values_to = "value") %>%
            filter(recScen %in% c("ARRec", "PDOclimRec",
                                  "PDOcyclRec", "MICERec")) %>%
            group_by(Metric, nameHCR) %>%
            summarize(mean = mean(value, na.rm = TRUE),
                      median = median(value, na.rm = TRUE),
                      hi95 = quantile(value, probs = 0.95, na.rm = TRUE),
                      low05 = quantile(value, probs = 0.05, na.rm = TRUE))
```

Table of results by scenario across iterations
- mean
- median
- sd
- 5th percentile
- 95th percentile

### Comparison of PFMC control rules by scenario
```{r}
# Compare performance of HCR2 among scenarios -----------------------------

annualRelBioCat %>% filter(HCR %in% c("HCR1", "HCR2")) %>%
  pivot_longer(cols = c(relAnnBioMax, relAnnCatMax), names_to = "Metric",
               values_to = "relAnn") %>%
  group_by(recScen, HCR, Metric) %>%
  summarize(meanRel = mean(relAnn),
            medRel = median(relAnn),
            hiRel = quantile(relAnn, probs = 0.975),
            loRel = quantile(relAnn, probs = 0.025),
            q1Rel = quantile(relAnn, probs = 0.25),
            q3Rel = quantile(relAnn, probs = 0.75),
            nRel = n()) %>% 
  ggplot(aes(x = recScen, fill = HCR)) +
  geom_boxplot(aes(ymin = loRel, lower = q1Rel, middle = medRel, 
                   upper = q3Rel, ymax = hiRel),
               stat = "identity") +
  theme_minimal() +
  facet_wrap(~Metric, scales = "free") +
  scale_fill_manual(values = hcrPal[2:3], labels = hcrLabels[2:3]) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
  # labs(y = "Annual Age1+ Biomass:Max in Poor Recruitment Iters", x = "HCR")

rebuildTime %>% filter(HCR %in% c("HCR1", "HCR2")) %>% 
  pivot_longer(cols = c(nClosures, meanRebuildTime, medRebuildTime), 
               names_to = "Metric", values_to = "value") %>%
  group_by(recScen, HCR, Metric) %>%
  summarize(meanRebuild = mean(value),
            medRebuild = median(value),
            hiRebuild = quantile(value, probs = 0.975),
            loRebuild = quantile(value, probs = 0.025),
            q1Rebuild = quantile(value, probs = 0.25),
            q3Rebuild = quantile(value, probs = 0.75),
            nRebuild = n()) %>% 
  ggplot(aes(x = recScen, fill = HCR)) +
  geom_boxplot(aes(ymin = loRebuild, lower = q1Rebuild, middle = medRebuild, 
                   upper = q3Rebuild, ymax = hiRebuild),
               stat = "identity") +
  theme_minimal() +
  facet_wrap(~Metric, scales = "free") +
  scale_fill_manual(values = hcrPal[2:3], labels = hcrLabels[2:3]) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

metricsTbl %>% filter(HCR %in% c("HCR1", "HCR2")) %>% 
  pivot_longer(cols = c(closuresFreq, collapseFreq, bonanzaFreq, 
                        meanCollapseSever, rebuildLengthMax), 
               names_to = "Metric", values_to = "value") %>%
  group_by(recScen, HCR, Metric) %>%
  summarize(meanRebuild = mean(value),
            medRebuild = median(value),
            hiRebuild = quantile(value, probs = 0.975),
            loRebuild = quantile(value, probs = 0.025),
            q1Rebuild = quantile(value, probs = 0.25),
            q3Rebuild = quantile(value, probs = 0.75),
            nRebuild = n()) %>% 
  ggplot(aes(x = recScen, fill = HCR)) +
  geom_boxplot(aes(ymin = loRebuild, lower = q1Rebuild, middle = medRebuild, 
                   upper = q3Rebuild, ymax = hiRebuild),
               stat = "identity") +
  theme_minimal() +
  facet_wrap(~Metric, scales = "free") +
  scale_fill_manual(values = hcrPal[2:3], labels = hcrLabels[2:3]) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

## Confusion tables

- Discrimination at cutoff threshold (150,000 mt)
```{r, cutoffConf}
# Terminal estimate relative error
termRE <- errCompare %>% filter(year == emYear.x | plotGroup == "ATsurvey") %>%
            select(age1plusEM, age1plusOM, errSmryBio, year, model_run.x, nameHCR,
                   iteration, scenario, HCR, recScen, plotGroup, recDevState) %>%
            mutate(closeYr = age1plusOM < 150000,
                   closeYrEst = age1plusEM < 150000,
                   collapseYr = age1plusOM < 50000,
                   collapseYrEst = age1plusEM < 50000,
                   recDevState = factor(recDevState, levels = c("high", "avg", "poor")))

# Confusion matrix
confErr <- termRE %>% filter(plotGroup != "non-convrg") %>%
  group_by(year, iteration, scenario, nameHCR, HCR, recScen) %>%
  mutate(closeTruePos = isTRUE(closeYr) & isTRUE(closeYrEst),
         closeFalsePos = isFALSE(closeYr) & isTRUE(closeYrEst),
         closeTrueNeg = isFALSE(closeYr) & isFALSE(closeYrEst),
         closeFalseNeg = isTRUE(closeYr) & isFALSE(closeYrEst),
         collapseTruePos = isTRUE(collapseYr) & isTRUE(collapseYrEst),
         collapseFalsePos = isFALSE(collapseYr) & isTRUE(collapseYrEst),
         collapseTrueNeg = isFALSE(collapseYr) & isFALSE(collapseYrEst),
         collapseFalseNeg = isTRUE(collapseYr) & isFALSE(collapseYrEst),
         closePropFalsePos = closeFalsePos * (errSmryBio/100),
         closePropFalseNeg = closeFalseNeg *(errSmryBio/100),
         collapsePropFalsePos = collapseFalsePos * (errSmryBio/100),
         collapsePropFalseNeg = collapseFalseNeg *(errSmryBio/100)) %>%
  group_by(scenario, nameHCR, HCR, recScen) %>%
  summarize(closeTruePos = sum(closeTruePos),
            closeFalsePos = sum(closeFalsePos),
            closeTrueNeg = sum(closeTrueNeg),
            closeFalseNeg = sum(closeFalseNeg),
            collapseTruePos = sum(collapseTruePos),
            collapseFalsePos = sum(collapseFalsePos),
            collapseTrueNeg = sum(collapseTrueNeg),
            collapseFalseNeg = sum(collapseFalseNeg),
            closePropFalsePos = mean(closePropFalsePos)*100,
            closePropFalseNeg = mean(closePropFalseNeg)*100,
            collapsePropFalsePos = mean(collapsePropFalsePos)*100,
            collapsePropFalseNeg = mean(collapsePropFalseNeg)*100) %>%
  mutate(nAssess = closeTruePos + closeFalsePos + closeTrueNeg + closeFalseNeg, # change to just during closure
         nClose = closeTruePos + closeFalseNeg,
         nCollapse = collapseTruePos + collapseFalseNeg,
         closeErrRate = (closeFalsePos + closeFalseNeg)/nAssess,
         closeFalsePosRate = closeFalsePos/(nAssess-nClose),
         closeFalseNegRate = closeFalseNeg/nClose,
         collapseErrRate = (collapseFalsePos + collapseFalseNeg)/nAssess,
         collapseFalsePosRate = collapseFalsePos/(nAssess-nCollapse),
         collapseFalseNegRate = collapseFalseNeg/nCollapse,
         nameHCR = factor(nameHCR, levels = c("NoCat", "PFMCF018", "PFMCFSST", "ConstF",
                                              "Index", "Pikitch", "40-10", "DynPik", "Dyn40-10")),
         recScen = factor(recScen, levels = c("ARRec", "PDOcyclRec", 
                                              "MICERec", "PDOclimRec",
                                              "RegRec", "SSTRec", "invRegRec")))

# confusion table for cutoff discrimination
confErr %>% filter(nAssess, closeTruePos, closeFalsePos, closeTrueNeg, closeFalseNeg, 
                   nClose, closeErrRate, closeFalsePosRate, closeFalseNegRate,
                   nameHCR, recScen)
```

- Discrimination at collapse threshold (50,000 mt)
```{r, collapseConf}
# confusion table for collapse discrimination
confErr %>% filter(nAssess, collapseTruePos, collapseFalsePos, collapseTrueNeg, collapseFalseNeg, 
                   nCollapse, collapseErrRate, collapseFalsePosRate, collapseFalseNegRate,
                   nameHCR, recScen)
```