---
title: "Sardine MSE Results Summary"
author: "Robert Wildermuth"
date: "3/25/2022"
output:
  pdf_document: 
    toc: true
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, include=FALSE}
library(r4ss)
library(tidyverse)
library(RColorBrewer)

source("J:/Desiree/Sardine/SardineMSE/R/GetSumryOutput.R")
source("J:/Desiree/Sardine/SardineMSE/R/CalcPerformance.R")
source("J:/Desiree/Sardine/SardineMSE/R/CalcTermTS.R")
# source("C:/Users/r.wildermuth/Documents/FutureSeas/SardineMSE/R/GetSumryOutput.R")
# source("C:/Users/r.wildermuth/Documents/FutureSeas/SardineMSE/R/CalcPerformance.R")
# source("C:/Users/r.wildermuth/Documents/FutureSeas/SardineMSE/R/CalcTermTS.R")
```

```{r, GetResults, include=FALSE}
# run GetSumryOutput and CalcPerformance to get performance metrics

mseDir <- "J:/Desiree/Sardine/SardineScenarios"
# mseDir <- "C:/Users/r.wildermuth/Documents/FutureSeas/SardineScenarios"
termYr <- 2068

scenarios <- c("constGrow2001OM_constGrow2005EM_RegRecHCR0",
              "constGrow2001OM_constGrow2005EM_RegRecHCR1",
              "constGrow2001OM_constGrow2005EM_RegRecHCR2",
              "constGrow2001OM_constGrow2005EM_RegRecHCR3",
              "constGrow2001OM_constGrow2005EM_RegRecHCR5",
              "constGrow2001OM_constGrow2005EM_RegRecHCR6",
              "constGrow2001OM_constGrow2005EM_RegRecHCR7",
              "constGrow2001OM_constGrow2005EM_RegRecHCR8",

              "constGrow2001OM_constGrow2005EM_ARRecHCR0",
              "constGrow2001OM_constGrow2005EM_ARRecHCR1",
              "constGrow2001OM_constGrow2005EM_ARRecHCR2",
              "constGrow2001OM_constGrow2005EM_ARRecHCR3",
              #"constGrow2001OM_constGrow2005EM_ARRecHCR4",
              "constGrow2001OM_constGrow2005EM_ARRecHCR5",
              "constGrow2001OM_constGrow2005EM_ARRecHCR6",
              "constGrow2001OM_constGrow2005EM_ARRecHCR7",
              "constGrow2001OM_constGrow2005EM_ARRecHCR8",
              
              # "constGrow2001OM_constGrow2005EM_MeanRecHCR0",
              # "constGrow2001OM_constGrow2005EM_MeanRecHCR1",
              # "constGrow2001OM_constGrow2005EM_MeanRecHCR2",
              # "constGrow2001OM_constGrow2005EM_MeanRecHCR3",
              # "constGrow2001OM_constGrow2005EM_MeanRecHCR5",
              # "constGrow2001OM_constGrow2005EM_MeanRecHCR6",
              # "constGrow2001OM_constGrow2005EM_MeanRecHCR7",
              # "constGrow2001OM_constGrow2005EM_MeanRecHCR8",

              "constGrow2001OM_constGrow2005EM_SSTRecHCR0",
              "constGrow2001OM_constGrow2005EM_SSTRecHCR1",
              "constGrow2001OM_constGrow2005EM_SSTRecHCR2",
              "constGrow2001OM_constGrow2005EM_SSTRecHCR3",
              #"constGrow2001OM_constGrow2005EM_SSTRecHCR4",
              "constGrow2001OM_constGrow2005EM_SSTRecHCR5",
              "constGrow2001OM_constGrow2005EM_SSTRecHCR6",
              "constGrow2001OM_constGrow2005EM_SSTRecHCR7",
              "constGrow2001OM_constGrow2005EM_SSTRecHCR8",

             # 
             #  "constGrow2001OM_constGrow2005EM_ccPDORecHCR0",
             #  "constGrow2001OM_constGrow2005EM_ccPDORecHCR1",
             #  "constGrow2001OM_constGrow2005EM_ccPDORecHCR2",
             #  "constGrow2001OM_constGrow2005EM_ccPDORecHCR3",
             # # "constGrow2001OM_constGrow2005EM_ccPDORecHCR4",
             #  "constGrow2001OM_constGrow2005EM_ccPDORecHCR5",
             #  "constGrow2001OM_constGrow2005EM_ccPDORecHCR6",
             #  "constGrow2001OM_constGrow2005EM_ccPDORecHCR7",
             #  "constGrow2001OM_constGrow2005EM_ccPDORecHCR8")#,
              # 
              "constGrow2001OM_constGrow2005EM_PDOcyclRecHCR0",
              "constGrow2001OM_constGrow2005EM_PDOcyclRecHCR1",
              "constGrow2001OM_constGrow2005EM_PDOcyclRecHCR2",
              "constGrow2001OM_constGrow2005EM_PDOcyclRecHCR3",
              #"constGrow2001OM_constGrow2005EM_PDOcyclRecHCR4",
              "constGrow2001OM_constGrow2005EM_PDOcyclRecHCR5",
              "constGrow2001OM_constGrow2005EM_PDOcyclRecHCR6",
              "constGrow2001OM_constGrow2005EM_PDOcyclRecHCR7",
              "constGrow2001OM_constGrow2005EM_PDOcyclRecHCR8")#,
              # 
              # "constGrow2001OM_constGrow2005EM_MICERecHCR0",
              # "constGrow2001OM_constGrow2005EM_MICERecHCR1",
              # "constGrow2001OM_constGrow2005EM_MICERecHCR2",
              # "constGrow2001OM_constGrow2005EM_MICERecHCR3",
              # "constGrow2001OM_constGrow2005EM_MICERecHCR4",
              # "constGrow2001OM_constGrow2005EM_MICERecHCR5",
              # "constGrow2001OM_constGrow2005EM_MICERecHCR6",
              # "constGrow2001OM_constGrow2005EM_MICERecHCR7",
              # "constGrow2001OM_constGrow2005EM_MICERecHCR8")


  # smryOutputList <- GetSumryOutput(dirSSMSE = mseDir,
  #                                  scenarios = scenarios)
  # saveRDS(smryOutputList, 
  #         file = file.path(mseDir, "serverRandRec_ARRec_allHCRs_results.RDS"))
smryOutputList <- readRDS(file.path(mseDir, "serverRegARPDOcyclSST_allHCRs_results.RDS"))
  
performanceList <- CalcPerformance(smryOutputList)

metricsTbl <- performanceList$perfomanceMetrics
                   

```

# Model Dynamics
## Timeseries
Plot timeseries of age1+ biomass, catch, and recruitment 
```{r, Timeseries, include=FALSE}
# get terminal estimates of these values for timeseries plots
termTS <- CalcTermTS(smryOutputList, termYr = termYr) %>% 
              mutate(HCR = sub(pattern = ".*Rec","", scenario),
                               recScen = sub(pattern = "HCR.*","", scenario)) %>%
              mutate(recScen = sub(pattern = ".*EM_","", recScen))

omName <- grep("_OM", smryOutputList$tsSmry$model_run, 
                 fixed = TRUE, value = TRUE)[1]
hcrPal <- brewer.pal(10, "Set3")[-2]

```

### Biomass
Plots of simulated (OM) biomass of age 1+ fish with 80% confidence intervals (grey band), and individual trajectories (dotted lines). Under a no fishing strategy:

* Biomass recovers in all recruitment scenarios
    * Regime and SST recruitment reach higher mean biomass than historic levels (max 1.5 x 10^6 in 1999 estimated from PK's research model)
* The SST recruitment scenario has unreasonably high biomass and larger variation 

```{r, tsBiomass, echo=FALSE, warning=FALSE}

# timeseries plot for presentation
termTS %>% filter(model_run == omName, HCR == "HCR0") %>%
  select(Bio_smry, year, model_run, iteration, scenario, HCR, recScen) %>%
  group_by(year, scenario, HCR, recScen) %>%
  summarize(meanAge1Plus = mean(Bio_smry),
            lowAge1Plus = quantile(Bio_smry, probs = 0.1, na.rm = TRUE),
            hiAge1Plus = quantile(Bio_smry, probs = 0.9, na.rm = TRUE)) %>%
  ggplot(aes(x = year, y = meanAge1Plus)) +
  geom_line() +
  geom_ribbon(aes(ymin = lowAge1Plus, ymax = hiAge1Plus, alpha = 0.3)) +
  facet_grid(rows = vars(HCR), cols = vars(recScen)) +
  theme_minimal() +
  labs(x = "Year", y = "Age 1+ Biomass (mt)") +
  # add example trajectories
  geom_line(data = subset(termTS, model_run == omName & 
                            HCR == "HCR0" & 
                            iteration %in% sample(iteration, size = 5)),
            mapping = aes(x = year, y = Bio_smry, linetype = as.character(iteration))) +
  scale_linetype_manual(values = rep("dashed", 5)) +
  scale_color_manual(values = c("blue")) +
  theme(legend.position = "none")

# plot summary of biomass trajectories
termTS %>% filter(model_run == omName) %>%
  select(Bio_smry, year, model_run, iteration, scenario, HCR, recScen) %>%
  group_by(year, scenario, HCR, recScen) %>%
  summarize(meanAge1Plus = mean(Bio_smry),
            lowAge1Plus = quantile(Bio_smry, probs = 0.1, na.rm = TRUE),
            hiAge1Plus = quantile(Bio_smry, probs = 0.9, na.rm = TRUE)) %>%
  ggplot(aes(x = year, y = meanAge1Plus)) +
  geom_line() +
  geom_ribbon(aes(ymin = lowAge1Plus, ymax = hiAge1Plus, alpha = 0.3)) +
  facet_grid(rows = vars(HCR), cols = vars(recScen)) +
  theme_minimal()+ 
  theme(legend.position = "none")

```

### Recruitment
Samples of time series of recruitment deviations from 4 iterations. 

* The SST recruitment scenario is biased positive with higher deviations than historic period
  * Leads to much higher recruitment (numbers) overall compared to other recruitment scenarios
* The cyclic PDO and Regime scenarios don't have the same amount of interannual variability as historic or autocorrelated scenarios, but over the projection period reach the same distribution as historic recruitment deviations.

```{r, tsRecruitment, echo=FALSE, warning=FALSE}
# look at recruitment deviations
termTS %>% filter(model_run == omName,
                  HCR == "HCR0", iteration %in% sample(iteration, size = 4)) %>%
  ggplot(aes(x = year, y = rec_dev)) +
  geom_line(aes(linetype = as.character(iteration), color = as.character(iteration))) + 
  scale_linetype_manual(values = rep("solid", 50)) +
  guides(linetype = "none") +
  geom_hline(yintercept = 0, color = "grey") +
  facet_grid(rows = vars(iteration), cols = vars(recScen)) + 
  theme_minimal() +
  geom_vline(xintercept = 2019, color = "gray") +
  theme(legend.position = "none")

# plot summary of recruitment trajectories
termTS %>% filter(model_run == omName) %>%
  select(Value.Recr, year, model_run, iteration, scenario, HCR, recScen) %>%
  group_by(year, scenario, HCR, recScen) %>%
  summarize(meanRec = mean(Value.Recr),
            lowRec = quantile(Value.Recr, probs = 0.1, na.rm = TRUE),
            hiRec = quantile(Value.Recr, probs = 0.9, na.rm = TRUE)) %>%
  ggplot(aes(x = year, y = meanRec)) +
  geom_line() +
  geom_ribbon(aes(ymin = lowRec, ymax = hiRec, alpha = 0.3)) +
  facet_grid(rows = vars(HCR), cols = vars(recScen)) +
  theme_minimal() +
  theme(legend.position = "none")

```

### Catch
* Catch generally follows the pattern of recruitment in each scenario
* Catch recovers more slowly in cyclic PDO scenario
* Catch reaches maximum levels in Regime and SST scenarios, almost immediately in SST scenario
  * Mean levels higher than AR scenario

```{r, tsCatch, echo=FALSE, warning=FALSE}
# plot summary of catch trajectories
termTS %>% filter(model_run == omName) %>%
  select(totCatch, year, model_run, iteration, scenario, HCR, recScen) %>%
  group_by(year, scenario, HCR, recScen) %>%
  summarize(meanCatch = mean(totCatch),
            lowCatch = quantile(totCatch, probs = 0.1, na.rm = TRUE),
            hiCatch = quantile(totCatch, probs = 0.9, na.rm = TRUE)) %>%
  ggplot(aes(x = year, y = meanCatch)) +
  geom_line() +
  geom_ribbon(aes(ymin = lowCatch, ymax = hiCatch, alpha = 0.3)) +
  facet_grid(rows = vars(HCR), cols = vars(recScen)) +
  theme_minimal() +
  theme(legend.position = "none")

# plot catch levels for HCR5 (Pikitch rule)
meanCat <- termTS %>% filter(model_run == omName, HCR == "HCR5") %>%
  select(totCatch, year, model_run, iteration, scenario, HCR, recScen) %>%
  # try non-zero catch summary
  filter(totCatch > 0) %>%
  group_by(year, scenario, HCR, recScen) %>%
  summarize(meanCatch = mean(totCatch),
            # lowCatch = quantile(totCatch, probs = 0.1, na.rm = TRUE),
            hiCatch = quantile(totCatch, probs = 0.9, na.rm = TRUE),
            minCatch = min(totCatch)) 

# termTS %>% filter(model_run == omName, HCR == "HCR5") %>%
#   ggplot(aes(x = year, y = totCatch)) +
#   geom_point() +
#   geom_line(data = meanCat, aes(y = meanCatch, color = HCR)) +
#   geom_line(data = meanCat, aes(y = minCatch, color = HCR)) +
#   facet_wrap(~recScen) +
#   scale_color_manual(values = hcrPal[5]) +
#   theme_minimal()
```

## Other parameters
* No real trend in mean age, though larger stock biomasses generally allow for potentially older mean ages
* Unfished biomass (B0) estimated to increase as simulation projection progresses under SST recruitment scenario

```{r, tsParams, echo=FALSE, warning=FALSE}
# compare to mean length
  # find columns for directory parsing
  dirsCol <- ncol(str_split(smryOutputList$ageComp$resDir, 
                            pattern = "/", simplify = TRUE))

fleet4Age <- smryOutputList$ageComp %>% 
                # need to parse out iteration, model run and scenario
                mutate(model_run = str_split(resDir, pattern = "/", 
                                             simplify = TRUE)[, dirsCol], 
                       iteration = as.integer(str_split(resDir, pattern = "/", 
                                             simplify = TRUE)[, dirsCol-1]), 
                       scenario = str_split(resDir, pattern = "/", 
                                            simplify = TRUE)[, dirsCol-2]) %>%
                filter(grepl(omName, model_run, fixed = TRUE), Yr > 2019,
                       Seas == 1, Fleet == 4)

termTS %>% filter(model_run == omName, year > 2019,
                  recScen == "ARRec") %>%
  left_join(y = fleet4Age, by = c("model_run", "iteration", "scenario", "year" = "Yr")) %>%
  ggplot(aes(x = log(Bio_smry), y = All_exp_mean, color = HCR, alpha = 0.05)) +
  geom_point() +
  facet_wrap(~HCR) + 
  theme_minimal() +
  scale_color_manual(values = hcrPal) +
  labs(y = "Mean Age in Survey", x = "Age1+ Biomass (log-mt)")


# Look at timeseries of B0 and account for non-convergence
smryOutputList$sclSmry %>% mutate(emYear = as.numeric(regmatches(model_run,
                                                        gregexpr("[[:digit:]]+", 
                                                                 model_run))),
                         HCR = sub(pattern = ".*Rec","", scenario),
                         recScen = sub(pattern = "HCR.*","", scenario)) %>%
  mutate(recScen = sub(pattern = ".*EM_","", recScen))  %>%
  filter(model_run != omName, HCR != "HCR0", max_grad < 0.01, 
         iteration == sample(1:max(unique(termTS$iteration)), size = 10)) %>%
  ggplot(aes(x = emYear, y = log(SSB_Unfished))) +
  geom_line(ggplot2::aes(linetype = as.character(iteration), color = HCR))+
    #ggplot2::scale_color_manual(values = c("#D65F00", "blue")) +
    ggplot2::scale_linetype_manual(values = rep("solid", 100)) +
  ggplot2::guides(linetype = "none") +
    ggplot2::facet_grid(rows = vars(HCR), cols = vars(recScen)) +
    ggplot2::theme_classic() + 
  #geom_rug(data = convrgCheck, mapping = aes(x = emYear),
  #                     sides = "b", inherit.aes = FALSE) +
  labs(x = "Year", y = "B0 (Unfished SSB)")

```

# Performance Metrics
Plot comparisons across HCR and Recruitment scenario

## Stock Status

* Larger variation in biomass outcomes among scenarios than HCRs
* Relative to other HCRs within recruitment scenarios, HCR1 allows larger biomasses on average
  * Distant second is HCR7, though groups more with other HCRs
  * HCR2 (Current SST rule) results in lowest mean biomass
* HCR1 allows for higher biomass than No Catch HCR0 in a few instances
* Collapse severity slightly higher in HCR3 and HCR8
* Slightly higher mean min ages and lengths in HCR0 and HCR1 

```{r, metricsStatus, echo=FALSE, warning=FALSE}
# parse out HCR and recruitment scenario
metricsTbl <- metricsTbl %>% mutate(HCR = sub(pattern = ".*Rec","", scenario),
                                    recScen = sub(pattern = "HCR.*","", scenario)) %>%
                mutate(recScen = sub(pattern = ".*EM_","", recScen),
                       nameHCR = case_when(HCR == "HCR0" ~ "NoCat",
                                           HCR == "HCR1" ~ "PFMCF018",
                                           HCR == "HCR2" ~ "PFMCFSST",
                                           HCR == "HCR3" ~ "ConstF",
                                           HCR == "HCR5" ~ "Pikitch",
                                           HCR == "HCR6" ~ "40-10",
                                           HCR == "HCR7" ~ "DynPik",
                                           HCR == "HCR8" ~ "Dyn40-10"))

# Calculate relative biomass and catch metrics
relDenoms <- metricsTbl %>% group_by(recScen, iteration) %>%
                summarize(maxMeanBio = max(meanB1plus),
                          maxMeanCat = max(meanCatch)) %>%
                full_join(y = metricsTbl %>% filter(HCR == "HCR0") %>% 
                                select(recScen, iteration, meanB1plus),
                          by = c("recScen", "iteration")) %>%
                rename("meanHCR0Bio" = "meanB1plus")

metricsTbl <- metricsTbl %>% full_join(y = relDenoms,
                                       by = c("recScen", "iteration")) %>%
                mutate(relBioMax = meanB1plus/maxMeanBio,
                       relBioHCR0 = meanB1plus/meanHCR0Bio,
                       relCatMax = meanCatch/maxMeanCat)

# fxn for metrics comparison
metricsPlot <- #function(yAxis, yLab){
  #ggplot(aes(x = HCR, y = vars(yAxis))) +
  ggplot() +
  geom_hline(yintercept = c(50000, 150000), color = "red") +
  geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = c("NoCat", "PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
#}

# plot mean biomass
yLab = "Mean Age1+ Biomass (mt)"
metricsTbl %>% #filter(recScen == "RandRec", HCR != "HCR4") %>%
  ggplot(aes(x = HCR, y = meanB1plus)) +
  geom_hline(yintercept = c(50000, 150000), color = "red") +
  geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = c("NoCat", "PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = yLab, x = "HCR") 

metricsTbl %>% #filter(recScen == "RandRec", HCR != "HCR4") %>%
  ggplot(aes(x = HCR, y = relBioMax)) +
  #geom_hline(yintercept = c(50000, 150000), color = "red") +
  geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = c("NoCat", "PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Mean Age1+ Biomass:Max", x = "HCR") 

metricsTbl %>% #filter(recScen == "RandRec", HCR != "HCR4") %>%
  ggplot(aes(x = HCR, y = relBioHCR0)) +
  #geom_hline(yintercept = c(50000, 150000), color = "red") +
  geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = c("NoCat", "PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Mean Age1+ Biomass:HCR0", x = "HCR") 

# plot collapse severity
metricsTbl %>% ggplot(aes(x = HCR, y = meanCollapseSever)) +
  geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = c("NoCat", "PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Collapse severity", x = "HCR") 

# plot mean minimum age
metricsTbl %>% ggplot(aes(x = HCR, y = minAge)) +
  geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = c("NoCat", "PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Mean minimum age", x = "HCR") 

# plot mean minimum length
metricsTbl %>% ggplot(aes(x = HCR, y = minLen)) +
  geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = c("NoCat", "PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Mean minimum length", x = "HCR") 
```

## Fishery

* Larger variation in catch outcomes among scenarios than HCRs
* Relative to HCR2 (highest mean catch), HCR1 and HCR7 had lowest mean catches
* HCR2 had highest catch variability in non-SST scenarios and lowest in SST scenario
  * HCR1 and HCR7 had highest variability in SST scenario
* Rank of least frequently below 150K mt: HCR0, HCR1, HCR2, HCR7
  * HCR1 had overall lowest frequency of years below 150K mt across all scenarios
* HCR1 least frequently below 50K mt, HCR3 and HCR8 most frequently below 50K mt
* Bonanzas (biomass >0.8B0) generally rare (<20% chance), except in SST scenario where bonanzas were common (50% chance or greater)
* Rebuilding time generally less than 10 yrs, though potentially longer in AR scenario
  * Slightly longer rebuilding time under HCR0 and HCR1 under Regime and cyclic PDO scenarios
  * Slightly longer rebuilding time under HCR3 and HCR8 under AR scenario
* Number of potential closure events always <4 for HCR0 and HCR1, no longer than 6 times

```{r, metricsCatch, echo=FALSE, warning=FALSE}
# plot mean catch
metricsTbl %>%  filter(HCR != "HCR0") %>%
  #filter(recScen == "RandRec", HCR != "HCR4") %>%
  ggplot(aes(x = HCR, y = meanCatch)) +
  geom_hline(yintercept = 200000) +
  geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal[-1], labels = c("PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Mean Catch (mt)", x = "HCR")

metricsTbl %>%  filter(HCR != "HCR0") %>%
  #filter(recScen == "RandRec", HCR != "HCR4") %>%
  ggplot(aes(x = HCR, y = relCatMax)) +
  #geom_hline(yintercept = 200000) +
  geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal[-1], labels = c("PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Mean Catch:Max", x = "HCR")

# plot catch sd
metricsTbl %>%  filter(HCR != "HCR0") %>%
  ggplot(aes(x = HCR, y = sdCatch)) +
  geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal[-1], labels = c("PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Catch SD (mt)", x = "HCR")

# plot closure frequency
metricsTbl %>% #filter(recScen == "RandRec", HCR != "HCR4") %>%
  ggplot(aes(x = HCR, y = closuresFreq)) +
  geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = c("NoCat", "PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Frequency Bt < 150,000 mt", x = "HCR")

# plot collapse frequency
metricsTbl %>% ggplot(aes(x = HCR, y = collapseFreq)) +
  geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = c("NoCat", "PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Frequency Bt < 50,000 mt", x = "HCR")


# plot bonanza frequency
metricsTbl %>% ggplot(aes(x = HCR, y = bonanzaFreq)) +
  geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = c("NoCat","PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Frequency Bt > 0.8B0", x = "HCR")

```

Investigate rebuilding lengths

```{r, echo=FALSE}
rebuildTime <- performanceList$tsSmry %>% select(Bio_smry , year, model_run, iteration, scenario, closure, closureLength) %>%
  filter(closure) %>% arrange(scenario, iteration, year) #%>% filter(year == 2020)
#all(rebuildTime$closure)
rebuildTime$isRebuilt <- NA
for(i in 1:(nrow(rebuildTime)-1)){
  rebuildTime$isRebuilt[i] <- if(rebuildTime$closureLength[i] != rebuildTime$closureLength[i+1]-1){
                              TRUE
                            } else { FALSE }
}
rebuildTime <- rebuildTime %>% filter(isRebuilt, year != 2069) %>% # remove last year b/c can't guarantee stock is rebuilt
                   mutate(HCR = sub(pattern = ".*Rec","", scenario),
                          recScen = sub(pattern = "HCR.*","", scenario)) %>%
                   mutate(recScen = sub(pattern = ".*EM_","", recScen))

rebuildTime %>%  
  ggplot(aes(x = HCR, y = closureLength)) +
  #geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  geom_dotplot(binaxis = "y", binwidth = 1/15) +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = c("NoCat","PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Rebuilding Time (yrs)", x = "HCR")

rebuildTime <- rebuildTime %>% group_by(model_run, iteration, scenario, HCR, recScen) %>%
                  summarize(nClosures = n(),
                            meanRebuildTime = mean(closureLength)) 

rebuildTime %>% #filter(recScen == "RandRec", HCR != "HCR4") %>% 
  ggplot(aes(x = HCR, y = meanRebuildTime)) +
  geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = c("NoCat","PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Mean Rebuilding Time (yrs)", x = "HCR")

rebuildTime %>%  
  ggplot(aes(x = HCR, y = nClosures)) +
  geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal, labels = c("NoCat","PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Number of Closures", x = "HCR")
```

## Assessment
* Maximum non-convergence rate was 2% to 6% depending on the HCR
* For the overall assessment:
  * Any given assessment was expected to be positively biased (up to 12.5%) over assessment years
  * The SST scenario was expected to be least biased for a given assessment year
* Relative error was expected to be unbiased for any given year at 95% CI in all but later years of SST scenario
* Estimates of biomass in the final year of assessment were negatively biased
  * SST recruitment scenario was most negatively biased

```{r, metricsAssess, echo=FALSE, warning=FALSE}

# plot convergence frequency
metricsTbl %>% filter(HCR != "HCR0") %>%
  ggplot(aes(x = HCR, y = frqNonConvg)) +
  geom_violin(aes(fill = HCR), draw_quantiles = c(0.1, 0.5, 0.9)) +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_fill_manual(values = hcrPal[-1], labels = c("PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Frequency of Non-convergence", x = "HCR")

hcrs <- unique(termTS$HCR)
exIters <- sample(termTS$iteration, size = 4)

convrgCheck <- smryOutputList$sclSmry %>% 
                  select(max_grad, model_run, iteration, scenario) %>%
                  mutate(emYear = as.numeric(regmatches(model_run,
                                                        gregexpr("[[:digit:]]+", 
                                                                 model_run))),
                         HCR = sub(pattern = ".*Rec","", scenario),
                         recScen = sub(pattern = "HCR.*","", scenario)) %>%
                  mutate(recScen = sub(pattern = ".*EM_","", recScen))  

cnvrgTS <- smryOutputList$tsSmry %>% mutate(HCR = sub(pattern = ".*Rec","", scenario),
                                   recScen = sub(pattern = "HCR.*","", scenario)) %>%
      mutate(recScen = sub(pattern = ".*EM_","", recScen)) %>%
      left_join(y = convrgCheck, by = c("iteration", "model_run", "scenario", "HCR", "recScen")) %>%
      mutate(plotGroup = case_when(model_run == omName ~ "OM",
                                   max_grad > 0.01 ~ "non-convrg",
                                   max_grad < 0.01 ~ "convrg"))


errCompare <- cnvrgTS %>% filter(Seas == 1, model_run != omName) %>%
                select(Bio_smry, year, model_run, iteration, scenario, HCR, 
                       recScen, emYear, plotGroup) %>%
                inner_join(y = subset(termTS, model_run == omName), 
                           by = c("year", "iteration", "scenario", "HCR", "recScen")) %>%
                #filter(iteration == 1) %>%
                  rename(age1plusOM = Bio_smry.y,
                         age1plusEM = Bio_smry.x) %>% 
                  mutate(errSmryBio = ((age1plusEM - age1plusOM)/age1plusOM)*100)

# Error among years within assessment
assessRE <- errCompare %>% filter(year <= emYear.x) %>%
                select(age1plusEM, age1plusOM, errSmryBio, year, model_run.x, iteration, scenario, HCR, recScen, plotGroup) %>%
                group_by(model_run.x, iteration, scenario, HCR, recScen, plotGroup) %>%
                summarize(meanRunRE = mean(errSmryBio),
                          medRunRE = median(errSmryBio),
                          hiRunRE = quantile(errSmryBio, probs = 0.95),
                          loRunRE = quantile(errSmryBio, probs = 0.05),
                          nErrs = n()) 
                # group_by(iteration, scenario, HCR, recScen, plotGroup) %>%
                # summarize(runMSE = mean(runMSE))  %>%
                # group_by(scenario, HCR, recScen, plotGroup) %>%
                # summarize(runMSE = mean(runMSE))

# Error among assessments within year
annualRE <- errCompare %>% filter(year <= emYear.x) %>%
                select(age1plusEM, age1plusOM, errSmryBio, year, model_run.x, iteration, scenario, HCR, recScen, plotGroup) %>%
                group_by(year,  scenario, HCR, recScen, plotGroup) %>%#iteration,
                summarize(meanYrRE = mean(errSmryBio),
                          medYrRE = median(errSmryBio),
                          hiYrRE = quantile(errSmryBio, probs = 0.975),
                          loYrRE = quantile(errSmryBio, probs = 0.025),
                          q1YrRE = quantile(errSmryBio, probs = 0.25),
                          q3YrRE = quantile(errSmryBio, probs = 0.75),
                          nErrs = n())

assessRE %>% filter(plotGroup != "non-convrg") %>%
  ggplot(aes(x = HCR, y = meanRunRE, fill = plotGroup)) +
  geom_boxplot() +
  facet_wrap(~recScen) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(title = "Mean Relative Error of Total Assessment")

scens <- unique(annualRE$recScen)
for(i in 1:length(scens)){
  print(annualRE %>% filter(plotGroup != "non-convrg", recScen == scens[i]) %>%
    ggplot(aes(x = as.factor(year), fill = HCR)) +
    geom_boxplot(aes(ymin = loYrRE, lower = q1YrRE, middle = medYrRE, 
                     upper = q3YrRE, ymax = hiYrRE),
                 stat = "identity") +
    facet_wrap(~HCR) +
    geom_hline(yintercept = 0) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    labs(title = paste("Median Annual Relative Error of Assessment,", scens[i], sep = " ")))
}

# Terminal estimate relative error
termRE <- errCompare %>% filter(year == emYear.x) %>%
              select(age1plusEM, age1plusOM, errSmryBio, year, model_run.x, iteration, scenario, HCR, recScen, plotGroup) %>%
              group_by(model_run.x, iteration, scenario, HCR, recScen, plotGroup) %>%
              summarize(termRE = mean(errSmryBio))

termRE %>% filter(plotGroup != "non-convrg") %>%
  ggplot(aes(x = HCR, y = termRE, fill = HCR)) +
  geom_boxplot() +
  facet_wrap(~recScen) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(title = "Mean Relative Error of Terminal Assessment Year") +
  scale_fill_manual(values = hcrPal[-1], labels = c("PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10"))

# termRE %>% group_by(scenario, HCR, recScen, plotGroup) %>%
#               summarize(termScenHCR_RE = mean(termRE),
#                         itN = n())

# Terminal lag1 estimate relative error
lag1RE <- errCompare %>% filter(year == (emYear.x - 1)) %>%
              select(age1plusEM, age1plusOM, errSmryBio, year, emYear.x, model_run.x, iteration, scenario, HCR, recScen, plotGroup) %>%
              group_by(model_run.x, iteration, scenario, HCR, recScen, plotGroup) %>%
              summarize(lag1RE = mean(errSmryBio))

lag1RE %>% filter(plotGroup != "non-convrg") %>%
  ggplot(aes(x = HCR, y = lag1RE, fill = HCR)) +
  geom_boxplot() +
  facet_wrap(~recScen) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(title = "Mean Relative Error of Assessment Year Lag1") +
  scale_fill_manual(values = hcrPal[-1], labels = c("PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10"))

# Terminal lag2 estimate relative error
lag2RE <- errCompare %>% filter(year == (emYear.x - 2)) %>%
              select(age1plusEM, age1plusOM, errSmryBio, year, emYear.x, 
                     model_run.x, iteration, scenario, HCR, recScen, plotGroup) %>%
              group_by(model_run.x, iteration, scenario, HCR, recScen, plotGroup) %>%
              summarize(lag2RE = mean(errSmryBio))

lag2RE %>% filter(plotGroup != "non-convrg") %>%
  ggplot(aes(x = HCR, y = lag2RE, fill = HCR)) +
  geom_boxplot() +
  facet_wrap(~recScen) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(title = "Mean Relative Error of Assessment Year Lag2") +
  scale_fill_manual(values = hcrPal[-1], labels = c("PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10"))

# Terminal lag3 estimate relative error
lag3RE <- errCompare %>% filter(year == (emYear.x - 3)) %>%
              select(age1plusEM, age1plusOM, errSmryBio, year, emYear.x, 
                     model_run.x, iteration, scenario, HCR, recScen, plotGroup) %>%
              group_by(model_run.x, iteration, scenario, HCR, recScen, plotGroup) %>%
              summarize(lag3RE = mean(errSmryBio))

lag3RE %>% filter(plotGroup != "non-convrg") %>%
  ggplot(aes(x = HCR, y = lag3RE, fill = HCR)) +
  geom_boxplot() +
  facet_wrap(~recScen) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(title = "Mean Relative Error of Assessment Year Lag3") +
  scale_fill_manual(values = hcrPal[-1], labels = c("PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10"))

# Forecast estimate relative error
foreRE <- errCompare %>% filter(year == (emYear.x + 1)) %>%
              select(age1plusEM, age1plusOM, errSmryBio, year, emYear.x, 
                     model_run.x, iteration, scenario, HCR, recScen, plotGroup) %>%
              group_by(model_run.x, iteration, scenario, HCR, recScen, plotGroup) %>%
              summarize(foreRE = mean(errSmryBio))

foreRE %>% filter(plotGroup != "non-convrg") %>%
  ggplot(aes(x = HCR, y = foreRE, fill = HCR)) +
  geom_boxplot() +
  facet_wrap(~recScen) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(title = "Mean Relative Error of Assessment 1 Year Forecast") +
  scale_fill_manual(values = hcrPal[-1], labels = c("PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10"))

```

### Error Progression
Plot some timeseries over estimation models for each run 

```{r, echo=FALSE}

for(hcr in 2:length(hcrs)){
  print(cnvrgTS %>% filter(HCR == hcrs[hcr], iteration %in% exIters, Seas == 1) %>%
      ggplot(aes(x = year, y = log(Bio_smry))) +
      ggplot2::geom_vline(xintercept = 2019, color = "gray") +
      ggplot2::geom_hline(yintercept = log(50000), color = "red") +
      ggplot2::geom_line(aes(linetype = model_run, color = plotGroup))+
      ggplot2::scale_color_manual(values = c("black", "blue", "#D65F00")) +
      ggplot2::scale_linetype_manual(values = rep("solid", 51)) +
      ggplot2::guides(linetype = "none") +
      ggplot2::facet_grid(rows = vars(iteration), cols = vars(recScen)) +
      ggplot2::theme_classic() + theme(legend.position="none") +
      labs(title = hcrs[hcr]))
}

age1PlusBio <- smryOutputList$tsSmry %>% filter(Seas == 1) %>%
                  select(year, Bio_smry, model_run, iteration, scenario) %>%
                  mutate(plotGroup = case_when(grepl("_OM", model_run, fixed = TRUE) ~ "OM",
                                               TRUE ~ "EM"))

age1PlusRE <- age1PlusBio %>% filter(plotGroup != "OM")
age1PlusRE <- age1PlusRE %>% pivot_wider(names_from = "plotGroup", values_from = "Bio_smry") %>%
                left_join(y = convrgCheck,
                          by = c("model_run", "iteration", "scenario")) %>%
                full_join(y = subset(age1PlusBio, subset = plotGroup == "OM"),
                          by = c("iteration", "scenario", "year")) %>%
                mutate(convrg = case_when(max_grad > 0.01 ~ "non-convrg",
                                          max_grad < 0.01 ~ "convrg",
                                          TRUE ~ "OM"),
                       emRE = (EM - Bio_smry)/Bio_smry * 100)

# Plot relative errors of biomass over time
for(hcr in 2:length(hcrs)){
  print(age1PlusRE %>% filter(HCR == hcrs[hcr], iteration %in% exIters) %>%
  ggplot(aes(x = year, y = ifelse(emRE > 100, 100, emRE))) + #y = emRE)) +
  geom_vline(xintercept = 2019, color = "gray") +
  geom_hline(yintercept = 0, color = "gray") +
  geom_line(aes(linetype = as.character(model_run.x), color = convrg))+
  scale_color_manual(values = c("black", "blue", "#D65F00")) +
  scale_linetype_manual(values = rep("solid", 51)) +
  guides(linetype = "none") +
  facet_grid(rows = vars(iteration), cols = vars(scenario)) +
  theme_classic() + ylab(label = "Relative Error of Age 1+ Biomass (%)") +
  labs(title = hcrs[hcr]) +
  ylim(-100, 100))
}
```

### Terminal Year Error
Error of final assessment year over projection 
```{r, echo=FALSE, warning=FALSE}
set.seed(seed = 413)
exIters <- sample(termTS$iteration, size = 3)
exHCR <- "HCR2"
convrgCheckEx <- convrgCheck %>% filter(iteration %in% exIters, HCR == exHCR)%>%
                  filter(max_grad > 0.01)

termTS %>% filter(iteration %in% exIters,
                  HCR == exHCR,
                  model_run != "constGrowBothShort_EM_init") %>%
  ggplot2::ggplot(aes(x = year, y = log(Bio_smry))) +
    ggplot2::geom_vline(xintercept = 2019, color = "gray") +
    
    ggplot2::geom_line(ggplot2::aes(linetype = as.character(iteration), color = model_run))+
    #ggplot2::scale_color_manual(values = c("#D65F00", "blue")) +
    ggplot2::scale_linetype_manual(values = rep("solid", 50)) +
  scale_fill_manual(labels = c("Terminal EM","OM")) +
    ggplot2::guides(linetype = "none") +
    ggplot2::facet_grid(rows = vars(iteration), cols = vars(recScen)) +
    ggplot2::theme_classic() + 
  geom_rug(data = convrgCheckEx, mapping = aes(x = emYear),
                       sides = "b", inherit.aes = FALSE) +
  labs(x = "Year", y = "Age1+ Biomass (log-t)")
```

# Tradeoffs
Plot tradeoffs among metrics

* HCR1 and HCR7 had relatively lower mean catch for a given mean level of biomass, while HCR2 and HCR8 had higher mean catch per biomass level
* On annual basis, stronger tradeoff between catch and biomass for HCRs 3, 6, 7, and 8
  * HCR2 provides higher catches at intermediate levels of biomass than many HCRs
* Positive relationship between mean catch and catch SD, except in SST scenario where relationship is negative

```{r, Tradeoffs, echo=FALSE, warning=FALSE}

metricsTbl %>% #filter(recScen == "RandRec", HCR != "HCR4") %>%
  ggplot(aes(x = log(meanCatch), y = log(meanB1plus), color = HCR)) +
  geom_vline(xintercept = log(200000)) +
  geom_hline(yintercept = log(150000)) +
  geom_point() +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_color_manual(values = hcrPal, labels = c("NoCat","PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  labs(y = "Mean Age 1+ Biomass (log-mt)", x = "Mean Catch (log-mt)",
       title = "Mean Biomass x Mean Catch") 

termTS %>% filter(model_run == omName, year > 2019) %>%
  ggplot(aes(x = log(Bio_smry), y = log(totCatch), color = HCR)) +
  geom_point() +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_color_manual(values = hcrPal, labels = c("NoCat","PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) +
  labs(y = "Catch (log-mt)", x = "Age1+ Biomass (log-mt)",
       title = "Annual Biomass x Annual Catch")

metricsTbl %>% ggplot(aes(x = log(meanCatch), y = closuresFreq, color = HCR)) +
  geom_point() +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_color_manual(values = hcrPal, labels = c("NoCat","PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) 

metricsTbl %>% ggplot(aes(x = meanCatch, y = sdCatch, color = HCR)) +
  geom_point() +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_color_manual(values = hcrPal, labels = c("NoCat","PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) 

metricsTbl %>% ggplot(aes(x = meanCatch, y = minLen, color = HCR)) +
  geom_point() +
  facet_wrap(~recScen) + 
  theme_minimal() +
  scale_color_manual(values = hcrPal, labels = c("NoCat","PFMCF018", "PFMCFSST",
                                                "ConstF", "Pikitch", "40-10",
                                                "DynPik", "Dyn40-10")) 

```



